\documentclass[11pt]{amsart}
\def\whole{}
\input{preamble}

\usepackage[notref,notcite]{showkeys}

\begin{document}

\maketitle

\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-1-2-3}    % D^b(PP^n) and Beilinson's resolution

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-4-5}      % Toric varieties and Cox rings

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-6}        % The Bondal-Thomsen collection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{comment}

\section{Secondary fan example}
\begin{center}
\begin{tikzpicture}[scale=1.5]
    % Define the points for easier reference
    \coordinate (A) at (1,0);
    \coordinate (B) at (2,0);
    \coordinate (C) at (0,1);
    \coordinate (D) at (0,-1);
    \coordinate (E) at (0,0);
    \coordinate (F) at (1.2,0.2);
    \coordinate (G) at (2.2,0.2);
    \coordinate (H) at (0.2,1.2);
    \coordinate (I) at (0.2,-.8);
    \coordinate (J) at (0.2,0.2);

    % Draw all line segments connecting the points
    \draw (A) -- (B) -- (C) -- cycle;
    \draw (A) -- (D) -- (C);
    \draw (B)--(D);
    \draw (A) -- (E);

    % Plot the points (as small black circles)
    \fill (A) circle (2pt);
    \fill (B) circle (2pt);
    \fill (C) circle (2pt);
    \fill (D) circle (2pt);
    \draw (.3,.3) node {$A$};
    \draw (.3,-.3) node {$B$};
\end{tikzpicture}
\end{center}

\end{comment}

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-7-8-9}    % The HHL resolution of the diagonal

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-10}       % Applications of the HHL Theorem

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-11}       % The secondary fan

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-12-13}    % The Cox category

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-14-15-16} % Proof of revised King's conjecture

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{sections/sections-17}       % Consequences of the revised King conjecture

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 18 (Matthias Zach): Tate resolutions over projective space}\label{lec:18-tate-resolutions-PPn}

Let $S = \k[x_0, \dots, x_n]$, $\Z$-graded with $\deg(x_i) = 1$, and let $E = \bigwedge_\k(e_0, \dots, e_n)$ be the exterior algebra with $\deg(e_i) = -1$. Let $\om_E$ denote the $\k$-dual of $E$. There are two reasons for this notation: first, $\om_E$ is the canonical module of the Gorenstein ring $E$; and second, it matches the notation of \cite{EFS}, which is the main reference for this lecture. We saw on Monday that there is an equivalence of categories
$
\RR \co D^b(S) \xra{\simeq} D^b(E)
$
that sends a finitely generated module $M$ (thought of as a complex concentrated in homological degree 0) to
\begin{equation}
\label{eqn:RMformula}
\RR(M) = \left[\cdots \xla{\del_\RR} \om_E(i) \otimes_\k M_{-i} \xla{\del_\RR} \om_E(i + 1) \otimes_\k M_{-i - 1} \xla{\del_\RR} \cdots \right],
\end{equation}
where $\om_E(i) \otimes_\k M_{-i}$ is in homological degree $-i$. Moreover, we saw that we get an induced equivalence
\begin{equation}
\label{eqn:geobgg}
\overline{\RR} \co D^b(\PP^n) \xra{\simeq} D^{\on{sing}}(E) \ce B \co D^b(E) / \Perf(E),
\end{equation}
where $D^{\on{sing}}(E)$ denotes the singularity category of $E$, and $\Perf(E)$ is the category of perfect complexes in $E$. Recall that the objects in $D^{\on{sing}}(E)$ are the same as those in $D^b(E)$, but the morphisms are obtained by inverting all morphisms in $D^b(E)$ whose mapping cone lies in $\Perf(E)$. The equivalence~\eqref{eqn:geobgg} gives a ``geometric" version of the BGG correspondence, though an unsatisfying one: the passage from $D^b(S)$ to $D^b(\PP^n)$ translates to the passage from $D^b(E)$ to $D^{\on{sing}}(E)$, which is only visible at the level of morphisms. Since the morphisms in $D^{\on{sing}}(E)$ are essentially unknowable, this renders the residual projective geometry in $D^{\on{sing}}(E)$ effectively invisible. This problem is solved by Eisenbud-Fl\o ystad-Schreyer's theory of Tate resolutions~\cite{EFS}. The goal of this lecture is to explain this theory and gesture toward some of its applications.

There is a classical method for explicating the morphisms in a derived category, namely replacing it with an appropriate homotopy category. For instance, $D^b(E)$ is equivalent to the homotopy category $K^-(E)$ of complexes of finitely generated graded free $E$-modules whose terms vanish in large homological degrees. In the case of an exterior algebra, this equivalence may be given by taking the $\k$-dual of a minimal free resolution. There is a similar result for the singularity category, due to Buchweitz~\cite{buc21}*{Theorem 4.4.1}: there is an equivalence
\begin{equation}
\label{eqn:buchweitz}
D^{\on{sing}}(E) \xra{\simeq} K(E),
\end{equation}
where $K(E)$ is the homotopy category of (possibly unbounded on both sides) exact complexes of finitely generated graded free $E$-modules. One way to model this equivalence is as follows. First note that it makes sense to take a (minimal) free resolution of any complex of finitely generated $E$-modules with bounded homology. With this in mind, the equivalence~\eqref{eqn:buchweitz} sends an object $C$ in $D^{\on{sing}}(E)$ to the mapping cone of the canonical quasi-isomorphism $f \co G \to F$, where $G$ is the minimal free resolution of the $\k$-dual of $N$, and $F$ is the $\k$-dual of the minimal free resolution of~$N$. One then arrives at the following key commutative diagram:
\begin{equation}
\label{eqn:tatediagram}
\xymatrix{
D^b(S) \ar[d] \ar[r]_-{\simeq}^-{\RR} & D^b(E) \ar[d] \ar[r]_-{\simeq} & K^-(E) \ar[d] \\
D^b(\PP^n) \ar[r]^-{\overline{\RR}}_-{\simeq} & D^{\on{sing}}(E) \ar[r]_-{\simeq}^B & K(E). \\
}
\end{equation}
The only functor here we have not yet described is the rightmost vertical one, which sends an object~$F$ to $\cone(G \xra{\simeq} F)$, where $G$ is the minimal free resolution of~$F$.

With all this in mind, let us now give an alternative formulation of the BGG correspondence for~$\PP^n$. Let $\F$ be a coherent sheaf on $\PP^n$ of Castelnuovo-Mumford regularity $r$, and let $M$ be a finitely generated graded $S$-module such that $\widetilde{M} = \F$. Let $G$ be the minimal free resolution of $\RR(M_{\ge r+1})$, and let $T(\F)$ be the mapping cone of the quasi-isomorphism $G \xra{\simeq} \RR(M)$.

\begin{remark}
The complex $\RR(M_{\ge r+1})$ has homology only in degree $-r-1$, which makes the minimal free resolution $G$ especially easy to compute. Moreover, the quasi-isomorphism $G \xra{\simeq} \RR(M)$ is minimal: this is because $H^0_\m(M) = 0$, so no linear combination of the generators of the free $E$-module
\end{remark}

\begin{thm}
Let $\F$ be a coherent sheaf on $\PP^n$.
\begin{enumerate}
\item $T(\F) = (B \circ \overline{\RR})(\F)$.
\item $T(\F)$ is minimal.
\item For all $i, j \in \Z$, there is an isomorphism $T(\F)_i = \bigoplus_{j \in \Z} \om_E(i + j) \otimes_\k H^j(\PP^n, \FF(-i - j))$.
\end{enumerate}
\end{thm}

\begin{proof}
Part (1) follows from the commutativity of Diagram~\eqref{eqn:tatediagram}: the formula for $T$ lifts $\F$ to $D^b(S)$ and then applies the top two horizontal and right most vertical functors in the diagram. Part~(2) is nearly immediate: both $G$ and $\RR(M)$ are minimal, and the quasi-isomorphism $G \xra{\simeq} \RR(M)$ is minimal because $H^0_\m(M) = 0$: this guarantees that no linear combination of the generators of
\end{proof}

\begin{defn}\cite{EFS}
Given a coherent sheaf $\F$ on $\PP^n$, $T(\F)$ is called the \defi{Tate resolution of $\F$}.
\end{defn}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 19 (Sasha Zotine): Tate resolutions over toric varieties}\label{lec:19-tate-resolutions-toric}

\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{appendix}
\include{sections/appendix.tex}

\subsection{Wish List}
\begin{enumerate}
    \item  Add a simple proof that the free module degrees in BCHSY come from Bondal-Thomsen.
    \item  Mention that BCHSY works in the radical case and include an example (maybe an example where the defining ideal of $X\subseteq Y$ is radical but not prime, e.g. the case of a point in a fake projective plane, which appeared in Brown-Erman's paper.)
    \item
\end{enumerate}

\subsection{Work on Notes and an M2 package for the week of July 13}
Notes:
\begin{itemize}
\item Main focus for DE, JY, MS, LCH: 5-8, 10 need a lot of work then expand on 1-4

\item The BCHSY treatment of HHL res should be broken into 3 lectures (sect 6-8) (possible outline at head of sect 6)


\item comments only on 11-14 (except for Michael)

\item Lauren should be chief of the material on the secondary fan

\item DE will work on Achinger material --  in sect 5

\item Lectures 1-5 could use some significant fleshing out, especially if we want this to eventually be a standalone document.
\end{itemize}

M2 Package
\begin{itemize}
\item  Have the package for computing HHL resolutions of equivariant sheaves and toric subvarietes in good enough shape, including documentation, to share with all participants.

\item BT monads in M2?

\item  Include code for computing the secondary fan associated to a multigraded ring.

\item  Can we write code that would allow for Fourier-Mukai transforms of line bundles, as in the Transform Lemma?

\end{itemize}

\end{appendix}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
