\ifdefined\whole
\else
\documentclass{amsart}
\input{preamble}
\begin{document}
\fi


\def\alp{{ \lfloor \alpha \rfloor}}

\section{Lecture 6 (Andreas Hochenegger):  The Bondal-Thomsen Collection}
The Bondal-Thomsen collection is a natural set of line bundles on a toric variety $X = X(\Sigma)$ that can be characterized in several different ways.  The following definition is originally due to Bondal \cite{Bondal}.  Consider the short exact sequence

\begin{equation}\label{eqn:SESCl}
0\to M\overset{\alpha}{\longrightarrow} \ZZ^n \overset{\deg}{\longrightarrow} \Cl(X) \to 0,
\end{equation}
where the basis vectors of $\ZZ^{n}$ correspond to the rays of $\Sigma$. We write $\alpha_i$ for the projection of $\alpha$ onto the $i$-th basis vector of $\ZZ^{n}$, which we identify with the corresponding invariant divisor $D_{i}$. Expressed in terms of the pairing between $M$ and $N$ this is $\alpha_i(m) = \langle m, -u_i\rangle$ where $u_{i}$
is the first integral point on the $i$-th ray of $\Sigma$. By abuse of notation, we again write $\alpha_{i}$ for the natural extension of $\alpha_{i}$ to a map
$M\otimes \QQ\to \QQ$.

Further, 
we define $\lfloor \alpha \rfloor\colon M\otimes \QQ \to \ZZ^n$ by the formula:
\[
  \lfloor \alpha \rfloor(m) :=  \sum_{i} \lfloor \alpha_i(m) \rfloor D_i.
\]
Note that though $\alpha(m)$ maps to the trivial element of $\Cl(X)\otimes \QQ$, this may not be the case for $\lfloor \alpha \rfloor(m)$.

\begin{defn}\label{defn:BTcollection}
    The \defi{Bondal-Thomsen collection} $\Theta_X\subseteq \Cl(X)\otimes \QQ$ is the image of $\deg \circ \lfloor \alpha \rfloor$.
    Elements of $\Theta_{X}$ are called Bondal-Thomsen  classes.
 \end{defn}
 
Note that $\Theta_{X}$ actually depends only on the  Cox ring $k[\NN^{n}]$ with its grading,
not on the toric variety $X$.

If $m\in M$, then $\alp(m) = \alpha(m)$, and this  maps to $0$ in $\Cl(X)$, so we may
consider $\Theta_X$ as the image of the induced (nonlinear) map $(M\otimes \QQ) / M \to \Cl(X)$ which we also
call $\alp$. (This is where we need to regard the Bondal-Thomsen classes as living in $\Cl(X)\otimes \QQ$.)

\begin{example} Consider the case $X=\P^{2}$. Then $M=\ZZ^2$ and $\ZZ^{n} = \ZZ^{3} =  \oplus_{i=0}^{2} \ZZ D_{i}$, with $\deg(D_{i}) = 1 \in \Cl(\PP^{2}) = \ZZ$
for each $i$. 

The map $\alpha$ is represented by the matrix
    \[
    \begin{pmatrix}
        -1&0\\ 0&-1\\1&1
    \end{pmatrix} .
    \]   
    Thus
        \[
    \lfloor \alpha \rfloor (a,b) = \lfloor -a\rfloor D_0 + \lfloor -b\rfloor D_1 + \lfloor a+b \rfloor D_2.
    \]
    Identifying $\Cl(\PP^{2})$ with $\ZZ$ this becomes 
      \[
    \alp(a,b) =\lfloor -a\rfloor + \lfloor -b\rfloor + \lfloor a+b\rfloor .
    \]
    Any point in $(M\otimes \QQ)/ M$, can be represented uniquely by an element $(a,b)\in M\otimes \QQ^2$ with $0\leq a,b <1$.  Thus   the Bondal-Thomsen collection is the set
           \[
    \alp(a,b) =\lfloor -a\rfloor + \lfloor -b\rfloor + \lfloor a+b\rfloor \text{ with } (a,b) \in [0,1)^{2}
    \]

This is easy to compute and with $(a,b) \in [0,1)^{2}$ we have
$$
\alp(a,b) = \begin{cases}
0 & \text{if } a=b=0\\
-2& \text{if both } a,b \text{ are nonzero but } a+b<1\\
-1 & \text{otherwise.}
\end{cases}.
$$
Thus $\Theta_{\P^{2}} = \{-2, -1, 0\}$.
\end{example}

We can think of the Bondal-Thomsen classes as lattice points in the image
under the degree map of the product
of $(-1,0]^{n}\subset \RR^{n}$; such a convex set is called a \emph{zonotope}. 

\begin{defn}\label{defn:KoszulZonotope}
    The \defi{Bondal zonotope} is the locus
    \[
    \mathcal Z\ce\sum_{i} a_i \deg(D_i) \subseteq  \Cl(X)\otimes \RR \text{ with } a_i \in (-1,0].
    \]
\end{defn}

\begin{example}
    The Bondal zonotope of $\PP^2$ is the half-open interval $(-3,0] \subset \RR = \Cl(\P^{2})\otimes \RR$.\end{example}
    
\begin{thm}\label{thm:Bondal-Thomsen equivalences}
    The following conditions on an element $d\in \Cl(X)$ are equivalent:
    \begin{enumerate}
        \item  $d$ is a Bondal-Thomsen class.
        \item  $d$ is equivalent to a rational divisor of the form $\sum_{i} a_i D_i$ with $a_i \in (-1,0].$
        \item  $d\otimes 1 \in \Cl(X) \otimes \RR$  lies in the Bondal zonotope of $X$.
        \item  In case $X$ is smooth: $d$ represents a line bundle that appears as a direct summand of
        $F_{\ell,*}\cO_X$ for some $\ell$, or, equivalently, for every sufficiently divisible $\ell$. 
        \footnote{According to \cite[Remark 5.4]{HHL} this can be done in the simplicial case
        by using the toric stack in place of the variety.}
     \end{enumerate}
\end{thm}
\begin{proof}
(1) $\equiv$ (2):
As explained after Definition~\ref{defn:BTcollection}, the Bondal-Thomsen collection is the image of $(M\otimes \QQ)/M$ under the
map $\alp$, and every element of $(M\otimes \QQ)/M$ is represented by an element with coefficients in $(-1,0].$
\daniel{I think this is off. Every element in $(M\otimes \QQ)/M$ is represented by an element in $\QQ^{\dim X}$ with coefficients in $(-1,0]$ but we want an element in $\QQ^{\# \text{ of rays}}$ with coefficients in $(-1,0]$. By abuse of notation, write $\alpha$ also for the induced map $M\otimes \QQ \to \QQ^n$. I think the point is the following
\[
\lfloor \alpha\rfloor(m) - \alpha(m) =\sum_i \left( \lfloor \alpha_i(m)\rfloor - \alpha_i(m)\right)
\]
and $\lfloor \alpha_i\rfloor(m) - \alpha_i(m) \in (-1,0].$
}

(2) $\equiv$  (3): trivial.

(2) $\equiv$ (4) We follow the proof given in \cite[Theorem 1.1]{achinger}. We first show that 
$F_{\ell,*}\cO_X$ is a direct sum of line bundles. Since
 $X$ has an open
affine covering by affine spaces it suffices to treat the case $X = \AA^{n}$, and in this case
$F_{\ell,*}\cO_X$ is the polynomial ring $k[x_{1},...,x_{n}]$ regarded as a module over
$S := k[x_{1}^{\ell},\dots,x_{n}^{\ell}]$, which is obviously a direct sum of the rank 1 free modules
$x^{a}S$ for all multi-indices $a$ with entries $0\leq a_{i}<\ell$.

To see that these patch together,
note that for any sheaf $\cL$ on $X$ the sheaf $F_{\ell,*}\cL$ carries a natural action by the
group $G := \NN^{n}/\ell \NN^{n} \cong (\ZZ/\ell)^{n}$, acting by a character of $G$.
In the case of $\AA^{n}$ the summand $x^{a}S$ is the eigensheaf for eigenvalue $a$ and it follows
that there is no problem patching the summands across different open affine sets.

More generally, $F_{\ell,*}\cO_X(b)$ corresponds, when restricted to an open set $\AA^{n}$,
to $k[x_{1},\dots,x_{n}](b)$ regarded as an $S$-module, and this decomposes in the same way,
but with a shift by $b$.

To prove that the Bondal-Thomsen sheaves appear in the decomposition
of $F_{\ell,*}\cO_X$
we define exponents $m(e,d)$, for $d,e\in \Cl(X)$, by the formula
$$
F_{\ell,*}\cO_X(d) = \oplus_{e} \cO_{X}(e)^{\oplus m(e,d)},
$$
We must show that $m(e,0)$ is nonzero only when $e$ is a Bondal-Thomsen class; and that
every Bondal-Thomsen class appears when $\ell$ is sufficiently divisible.

From the push-pull formula we get
$$
F_{\ell,*} O_X(d)  \otimes \cO_{X}(-e)= F_{\ell,*}\cO_X(d-\ell e) \eqno{(1)}\label{pushpull}
$$
\noindent from which we see that $m(e,d) = m(0,d-\ell e)$ depends only on the difference $d-\ell e$.
Thus we define $m(d) := m(0,d)$. The desired conclusion will follow from the case $d=0$ of the following more general result:

\begin{lemma}\label{lem:Achinger's Lemma}
For $d,e\in \Cl(X)$, the number $m(e,d) = m(d-\ell e)$ is the number of  divisors  $D= \sum a_{i}D_{i}\in \ZZ^{n}$ with coefficients
$a_{i}$ in the interval $0\leq a_{i}<\ell$ such that $\deg D= d -\ell e$.
\end{lemma}

Here the $D_{i}$ are, as always, the natural basis of $\Div(X) = \ZZ^{n}.$ 
\begin{proof}
We first assume that $X$ is complete, so that $h^{0}(\cO_{X}(e))$ is finite-dimensional for all $e$ and
the effective divisors on $X$ lie in a pointed cone inside $\ZZ^{n}$. We form the generating function
$$
h^{0}(F_{\ell,*}\cO_X(d)) := \sum_{e\in \Cl(X) }m(e,d) h^{0}(\cO_{X}(e)) = \sum_{e\in \Cl(X)}m(d-\ell e) h^{0}(\cO_{X}(e)).
$$
  Fixing a basis $\{\cO_{X}(d_{i})\}_{i = 1,\dots,\rho}$ of $\Cl(X)\cong \ZZ^{\rho}$ we define formal power series
 $$
 s(t) = \sum_{a \in \ZZ^{\rho}} h^{0}( \cO_{X}(\sum_{i}a_{i}d_{i})) t^{a}, \qquad
 m(t) = \sum_{a \in \ZZ^{\rho}} m(\cO_{X}(\sum_{i}a_{i}d_{i})) t^{a}.
 $$
 where as usual $a = (a_{1}\dots,a_{\rho})$ is a multi-index.
From equation \eqref{pushpull} we get
$$
s(t) = m(t)s(t^{\ell}).
$$
%%%%%%%
Now $h^{0}(\cO_X(d))$ is the number of divisors $D\in \text{Div}(X) = \ZZ^{n}$ with $\deg(D) = d\in \Cl(X)$,
so
$$
s(t) = \sum_{D\in \NN^{n}} t^{\deg D} = \prod_{i = 1}^{n}\frac{1}{1-t^{\deg D_{i}}}.
$$
Thus
$$
m(t) = 
\frac{s(t)}{s(t^{\ell a})} = 
\prod_{i=1}^{n}\frac{1-t^{\ell \deg D_{i}}}{1 -t^{\deg D_{i}}} =
\prod_{i=1}^{n}(1+t^{\deg D_{i}}+\cdots + t^{(\ell-1)\deg D_{i}}).
$$
Comparing coefficients, it follows that 
$m(d)$ is the number of divisors $D$ with $\deg(D) = d\in \Cl(X)$ that have the form
 $D = \sum a_{i}D_{i}$ with $0\leq a_{i}< \ell$, completing the proof in the case when
 $X$ is complete.
 
 If $X$ is not complete, we add cones to the associated fan, and then subdivide, to get a birational embedding as an open subvariety
 $X \to \overline X$ where $\overline X$ is both complete and smooth. The pushforward functor commutes in an obvious sense with the inclusion. The class group of $\Cl(X)$ is the quotient of $\Cl(\overline X)$ by the classes coming from the new rays,
 and the restriction of a sum of line bundles on $\overline X$ to the open set $X$ simply deletes from the sum any line bundles that don't come from divisors on $X$; thus
 the desired formula for $X$ follows from the corresponding formula for $\overline X$.
 \end{proof}

\medskip\noindent {\it Conclusion of the Proof of Theorem~\ref{thm:Bondal-Thomsen equivalences}}\\
Applying Lemma~\ref{lem:Achinger's Lemma} in the case $d=0$, we see that $m(e,0)$ is nonzero
if and only if there is a divisor $D$ with $\deg D = -\ell e$ such that $D = \sum_{i} a_{i}D_{i}$ with $0\leq a_{i} < \ell$;
that is, $e = \deg(D/\ell)$, so that $e$ is a Bondal-Thomsen class, and every Bondal-Thomsen class appears for sufficiently divisible $\ell$. 
\end{proof}

We can use  Demazure's Vanishing Theorem \cite[Theorem 9.2.3]{CLS} to derive a useful vanishing theorem related to Bondal-Thomsen classes.
%\michael{This is (close to) \cite{king}*{Lemma 2.20}, which isn't that easy, right?}
\begin{thm}[Demazure Vanishing] \label{thm:demazure}
If $X$ is a simplicial, projective toric variety and $D$ is a nef $\QQ$-Cartier divisor on $X$, then
$H^p(X, \cO_{X}(\lfloor D \rfloor )) = 0$
for all $p > 0$.
\end{thm}
A similar statement holds for reasonable toric stacks; see \cite[Lemma 2.20]{king}.

\begin{prop}\label{prop:Demazure}
    Let $a\in \Cl(X)$ be a nef divisor class. If $-d\in \Theta_X$ is a Bondal-Thomsen class, then
    $
    H^p(X,\cO_X(a-d)) = 0 \text{ for all } p>0.
    $
\end{prop}
\begin{proof}
Choose an integral toric divisor $B=\sum_{i} \alpha_iD_i$, with $\alpha_i\in \ZZ$ whose class is $a-d$.  Since $-d$ is a Bondal-Thomsen class, we can choose a toric divisor $D=\sum_i \epsilon_iD_i$, where $\epsilon_i \in [0,1)$, whose class is $d$.

The $\QQ$-divisor $B+D$ is nef because its class is $(a-d)+d=a$.  And $\lfloor B+D\rfloor = B$ has class $a-d$.  By Theorem~\ref{thm:demazure},
    \[
    0 = H^p(X, \cO_{X}(\lfloor B+D \rfloor )) =  H^p(X, \cO_{X}(B)) =  H^p(X, \cO_{X}(a-d)).
    \]
\end{proof}

\begin{cor}\label{cor:BTNoCohom}
    If $-d\ \in \Theta_X$ is a Bondal-Thomsen class, then $H^i(X,\cO_X(-d))=0$ for all $i>0$.  If $X$ is complete and $d\ne 0$, then $H^0(X,\cO_X(-d))$ also vanishes.
\end{cor}
\begin{proof}
    For $p>0$, we can apply Proposition~\ref{prop:Demazure} with $a=0$.  When $d\ne 0$, $\cO_X(-d)$ is the negative of an effective divisor. Since $X$ is complete, the effective divisors lie in a pointed cone,  so 
    $\cO_X(-d)$ has no global sections.
\end{proof}


\begin{comment}

Claim:
There are 4 ways to think about the Bondal-Thomsen collection which we claim are all equivalent.

(1)  Via Bondal’s definition, i.e. as the image in Cl(X) of the map M\otimes \RR —> Cl(X) where the point \theta maps via the round-down formula in Definition 2.12 as in our King paper.  Specifically we send \theta \mapsto D(\theta) \ce \sum_\rho \lfloor <-\theta, u_\rho> \rfloor D_\rho.

(2)  As the elements in Cl(X) that are linearly equivalent (in Cl(X)\otimes RR) to a RR-divisor of the form \sum_{\rho} a_\rho D_{\rho} with with a_\rho \in (-1,0].

(3)  As the lattice points inside of the zonotope associated to (2).

(4)  As the summands of the pushforward under Frobenius.

Proof:
(2) <==> (3) is obvious.

(1) <==> (2) is as follows.   Let \theta \in M\otimes \RR and D(\theta) as in (1).  Define D’(\theta) by the same formula but without the round down. That is, D’(\theta) = \sum_\rho \lfloor -\theta, u_\rho \rfloor D_\rho is an \RR-divisor which is equivalent to 0 in Cl(X)\otimes RR.  This is because D’(\theta) is the image of \theta under the composition of maps in the exact sequence:

0—> M\otimes RR —> RR^{\Sigma(1)} —> Cl(X)\otimes RR —> 0

Now examine the coefficients of D - D’.  For each \rho, the coefficient of D-D’ is \lfloor <-\theta, u_\rho> \rfloor -  <-\theta, u_\rho>.  But for any real number \zeta, the difference \lfloor \zeta \rfloor - \zeta lies in the range (-1,0].  It follows So D(\theta) - D’(\theta) has the form of a divisor from (2).  Since D’(\theta) is linearly equivalent to 0, we obtain the result.

(2) <==> (4) is from Theorem 2 of Achinger 2015 (the D = 0 case), which is not so bad.

How does this look?

\end{comment}

\ifdefined\whole
\else
\bibliographystyle{plain}
\bibliography{Bibliography}
\end{document}
\fi

