%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifdefined\whole
\else
\documentclass{amsart}
\input{preamble}
\begin{document}
\fi

\section{Lecture 7 (Jason McCullough): Constructing the resolution and examples}\label{lec:7-HHL-construction}

\daniel{The notes in this section spill over into Lectures 7 and 8.  Need to subdivide, reframe etc.  A rough overview for how we want these three sections to look is the following:

\begin{itemize}
    \item  Lecture 7:  Focus on the construction of the resolution.  How are the terms and the differentials defined?  Give examples and get the audience familiar with the notation and with what is going on.  Probably focus primarily on simple cases, like a point in $\PP^1$, a point in $\PP^2$, a quadric in $\PP^2$, the twisted cubic.

    There's a choice to be made in this lecture:  
        \begin{itemize}
            \item Whether you then continue on into more complicated examples (like the diagonal $\PP^2\subseteq \PP^2 \times \PP^2$, etc). 
            \item  Whether you start to incorporate more nuanced properties of the resolution (e.g. that the free summands in the resolution correspond to Bondal-Thomsen degrees. -- this will now be mentioned in 7, proven in section 8.
        \end{itemize}

    \item  Lecture 8:  This lecture is focused on increasing the complexity of the examples considered and demonstrating some of the more subtle properties of the resolutions.  Where you starts depends on the final choice in the previous lecture.  You should demonstrate the resolution of the diagonal for a Hirzebruch surface of type 3, since that is a running example later on.

    We want to also communicate the fact that the resolution ``only depends on the rays''.  Stating that fact precisely is a little bit delicate; see Corollary~\ref{cor:diagonalUniform} for one attempt at such a statement.  But this fact is relevant to our later treatment of King's Conjecture.
    
    \item  Lecture 9: The goal of this lecture is to prove the theorem.  If  you determine that's too hard, then we should reassess.
\end{itemize}
}


This section is an introduction to the papers \cite{BCHSY} and \cite{BH25}.

\def\tF{{\widetilde \FF}}

The inclusion of one toric variety in another is defined by a 
homogeneous \emph{pure binomial prime ideal}
in the Cox ring of the target; that is, a prime generated by elements $x^m-x^p \in S := k[x_1,\dots, x_n]$, where $m,p\in\ZZ^n$ are multi-indices. By \cite{Eisenbud-Sturmfels}, primeness implies that
the set $L = \{m-p\mid x^m-x^p\in I \cdot k[\ZZ^n]\}$ is a saturated lattice and there is a one-to-one correspondence between pure binomial ideals that are prime and saturated lattices meeting
 $\NN^n$ only in 0. Such binomial ideals correspond to affine, not-necessarily normal, toric varieties in $\AA^{n}$. 
 
 The ring $R \ce S/I$ is isomorphic to the semigroup ring $k[\NN^n/L]$ where $\NN^n/L$ is the image of $\NN^n$ under the quotient map $\ZZ^n\rightarrow \ZZ^n/L$.
 In the case $M = L$ then after an additional choice of irrelevant ideal, $S$ becomes the Cox ring of a projective toric variety $X$ with class group $\ZZ^n/M$, in which case $I$ is the ideal corresponding to the subvariety consisting of the identity element of the dense torus. This example will be treated in the next section.


Theorem 3.4 of \cite{BCHSY} provides a canonical  resolution $\FF$ of the normalization $\overline R$
of the ring $R$. It is obtained by factoring out a regular sequence on a $\ZZ^{n}$-graded, $L$-equivariant $S$-free resolution $\widetilde \FF$ 
of an $S$-submodule generated by monomials in $k[\ZZ^n] \subset k(x_{1}, \dots, x_{n})$ (Definition~\ref{def:M_{L}}). Although the free modules in $\tF$ are not finitely generated, the quotient $\FF$
is a finite, $S$-free, $(\ZZ^{n}/L$-graded, resolution of length equal to the 
codimension of $I$, reproving the theorem of Hochster that
$\overline R$ is Cohen-Macaulay. Moreover, the free modules $\FF_{i}$ have degrees
corresponding to the Bondal-Thomsen classes defined in the previous section. It may be easiest to
absorb the following general definitions at the same time as the special case treated in Example~\ref{first example of the HHL resolution}.


The resolution $\tF$ is built from an infinite $L$-invariant cellular subdivision of $L_\RR \ce \RR\otimes L$
and a stratification on $L_{\RR}$.  Although \cite{BCHSY} treats a more general stratification, we will
treat only the case of  the ``ceiling stratification'' and the $\ZZ^{n}$-invariant subdivision of $L_\RR$ defined by the coordinate hyperplanes $H_i \ce \{x\in L_R\mid x_i = 0\}$, which divide $L_\RR$ into cells $A$ whose closures are convex polyhedra, meeting along their faces; see Figure~\ref{fig1}. 

%% , and the resulting $S$-free complex $\tilde{\FF}$ is $L$-graded and acquires through this the structure of an $S[L]$-module. The generators of the free modules in $\tilde \FF$ correspond to
%% chambers in this cell complex, and the $i$-th term of the complex $\tilde\FF$ is $\oplus S\cdot\sigma$, where
%% the direct sum runs over all cells of dimension $i$.

We regard the subdivision above as making $L_{\RR}$ into an infinite cell complex.
If $A$ is a cell, and $p = (p_1,\dots, p_n) \in \RR^n$ is a point in the
interior of $A$, then we give $A$ the weight
$$
\Psi(A) \ce \prod_{i=1}^n x_i^{\lceil p_i\rceil}\in \ZZ^{n};
$$
note that because the subdivision of $L$ is induced by the coordinate hyperplanes this
is independent of the choice of $p$. 

If $B$ is 
a cell in the boundary of the closure $\overline A$, then $B$ is the intersection of
$\overline A$ with some of the hyperplanes $H_{j}$. Thus any interior point of $B$ will
be a limit of points in the interior of $A$ where some coordinates become 0. It follows that
$\Psi(B)$ will be termwise less than or equal to $\Psi(A)$; in fact $\Psi(A) - \Psi(B)$ is a vector
of 0s and 1s.

We define the term of $\tF$ corresponding to a cell $A$ to be $S(-\Psi(A))$. The differential of the resolution $\tilde \FF$ is obtained by choosing
an orientation on $L_\RR$ and homogenizing the usual differential of
a cell complex $\partial_{\L_{\RR}}A = \sum\epsilon_{i}B_{i}$, where each $\epsilon_{i} = \pm 1$, according to weights assigned to the chambers. With this homogenization, the component of the differential that maps $S(-\Psi(A))$ to $S(-\Psi(B_{i}))$ is multiplication by $\epsilon_{i}x^{\Psi A - \Psi B_{i}}$. Thus the
differential preserves the $\ZZ^{n}$-grading. As the monomials assigned this way are $L$-invariant, the complex $\tF$ is $L$-invariant.


In particular,
$$
\tF_{0} = \bigoplus_{p \hbox{ is a vertex of the cell complex }L_{\RR}}S(-\Psi(p)),
$$
so there is a natural augmentation map from $\tF_{0}$ to a module $M_{L}$ generated by the corresponding monomials:

\begin{defn}\label{def:M_{L}}
 $M_{L}\subset k(x_{1}, \dots, x_{n})$ is the $S$-submodule generated by the monomials
 $$
 \{x^{\Psi(p)} \mid p \hbox{ is a vertex of the cell complex }L_{\RR}\}.
 $$
\end{defn}

In Theorem~\ref{thm:HHL resolution} we will prove that the complex $\tF$ is a resolution of $M_L$.

Because the differentials of $\tF$ are $L$-invariant we can form a quotient by the action of $L$. Proposition 3.3 of~\cite{BCHSY} shows moreover that the quotient of $M_L$ by this $L$-action is $\overline{R}$, regarded as a fractional ideal of $R$. 


%% For $1\neq z\in L$ the element $1-z\in S[L]$ is a nonzerodivisor on any $L$-graded $S[L]$ module. 
%% The  resolution $\FF$ is obtained by taking the quotient of $\tilde \FF$
%% by the regular sequence $1-z_1, \dots 1-z_m$, where $z_1,\dots, z_m$ are the elements of $L$ that are minimal in the sense that they
%% are not divisible by any variables in $S$.
%% Proposition 3.3 of~\cite{BCHSY} shows that the quotient of the monomial module $M_L$ by $L$ is a fractional ideal of $R$ that is
%% isomorphic to $\overline R$.

We now describe these resolutions in the two simplest cases: when $I = (x_1-x_2)$, so that $\overline R = R$, and when $I = (x_1^3-x_2^2)$, so that $\overline R = k[x_1,x_2/x_1]$. 
To simplify the notation we write $S =k[x,y]$ in place of $k[x_1,x_2]$.  

\begin{example}$R \ce k[x,y]/(x-y)$:\label{first example of the HHL resolution}
In this case the lattice $L$ is generated by the single vector $ (1,-1)\in \ZZ^2$,
which corresponds to the monomial $x/y$ if we regard $k[ZZ^{2}]$ as a subset of $k(x,y)$.
Since the cellular subdivision of $L_R$ is $L$-equivariant, it suffices to consider its restriction to  a fundamental domain for the action of $L$, which is contained
in a single square of the lattice $\ZZ^2$, as shown in Figure~\ref{fig1}.
In this special case, the construction is the same as that of the ``hull resolution" of \cite[Section 3]{Bayer-Sturmfels} (see also \cite[Sections 9.2--9.3]{MScomb}) of $R$.

\begin{figure}[h]\label{fig1}
$$\begin{tikzpicture}[scale=3]
  % Horizontal walls - blue
  \draw[blue] (0, 0) -- (1, 0);
  \draw[blue] (0,-1) -- (1,-1);

  % Vertical walls - red
  \draw[red] (0, 0) -- (0,-1);
  \draw[red] (1, 0) -- (1,-1);

  % Diagonal line - green
  \draw[green!70!black] (0,0) -- (1,-1);

  % Small dots at corners, labeled a
  \fill (0, 0) circle (.5pt) node[above left]  {$a:(0,0)$};
  \fill (1,-1) circle (.5pt) node[below right] {$b:(1,-1)$};

  % Larger dot at midpoint, labeled A
  \fill (1/4,-1/4) circle (1pt) node[above right] {$(1/4,-1/4)$};
  \fill (3/5,-3/5) circle (0pt) node[above right] {$A$};
\end{tikzpicture}
$$
  \caption{Diagram for the resolution of $k[x,y]/(x-y)$ on a fundamental domain}
\end{figure}
The set $L_R\subset \RR^2$ meets this fundamental domain in the diagonal line $A$ (the dot represents a general point of $A$, which gives the label of $A$). There are infinitely many 0-cells, which are $L$-translates of $a$, and infinitely many 1-cells, which are the $L$-translates of $A$. We choose an (L-invariant) orientation, and take the differential to be the usual one for a cell complex, homogenized by taking the upper left corner $a$  
to have weight $x^0y^0=1$, the lower right corner $b$ to have weight $x^1y^{-1}$ and 
 the cell $A$ to have weight given by the interior point  $p= (1/4, -1/4)$ so that $A$ has weight
$ \Psi(p) = x^{\lceil 1/4\rceil}y^{\lceil -1/4\rceil} = x^1y^0$. With these choices $\tF$ and its augmentation to $M_{L}$ have the form
$$
\tF := 0 \to 
\tF_{1} \xrightarrow{\tilde d(A)} 
\tF_{0} \rightarrow 
M_{L} = \sum_{m\in \ZZ} S\cdot (x^{m}/y^{m}) \rightarrow 0.
$$
where
$$
\tF_{i} = \begin{cases}
  \oplus_{\ell \in L} S(\ell(A))&\hbox{ if } i = 1\\
\oplus_{\ell \in L} S(\ell(a))&\hbox{ if } i = 0\\
\end{cases}
$$
 The differential  $\tilde d(A) $ may be written as
$\tilde d(A) = \sum_{\ell \in L}x^{\ell(a)}-y^{\ell(b)}$,
which makes sense because $b$ is the translate of $a$ by a generator of $L$.   
Taking the quotient by 
$L$ we obtain the usual two-term resolution $\FF: S(-1)\xrightarrow{d} S$, with map  $d = (x-y)$.

 Alternately, we could form the resolution $\FF$ by first taking the quotient of $L_{\RR}$ topologically, obtaining a circle,  and remembering the monomials associated to each map. This  gives a cell structure on a circle with a single 0-cell and a single 1-cell.
 \begin{figure}
 \[
 \begin{tikzpicture}\label{fig 2}
 \draw (0,0) circle (1cm);
 \fill (270:1cm) circle (2pt) node [below] {$a/b$};
 \fill (90:1cm) circle (4pt) node [below] {$A$};
 \draw[->] (100:1.1cm)  arc[radius=1.1cm,start angle=100, end angle = 180] node[above, midway] {$x$};
 \draw[->] (80:1.1cm) arc[radius=1.1cm,start angle=80, end angle = 0] node[above, midway] {$y$};
 \end{tikzpicture}
 \]
 \caption{Diagram for the resolution of $k[x,y]/(x-y)$ on the 1-torus}
 
\end{figure}

\end{example}

Here is a first example in which $R \neq \overline R$.

\begin{example} [The cuspidal cubic]
  $R\ce k[x,y]/(x^3-y^2) = k[t^{2},t^{3}$:
If $I = (x^3-y^2)$ then $L$ is generated by the single vector
$x^3/y^2 = (3,-2) \in \ZZ^2$, so
$L_\RR$ is the diagonal line in Figure~\ref{fig:cuspidal cubic 1}, which
shows the closure of a fundamental domain in $L_R$ for the action of $L$
on $\RR^n$.

The ring $R$ is not integrally closed: the integral closure is $\overline R = k[x^{2}/y^{3}] = k[t]$
\footnote{The $S$-free ``hull resolution" of of $R$ \cite[Section 3]{Bayer-Sturmfels} (see also \cite[Sections 9.2--9.3]{MScomb}) would be obtained, in this case, from the cell complex with one 1-cell and one 0-cell by considering the whole of the diagonal line in Figure~\ref{fig2} as a single 1-cell with weight $x^3$, and with vertices
$(0,0)$ (of weight 1) and $(2,3)$ (of weight $x^2/y^3$ only, yielding the 2-term complex with differential
$d = (x^3-y^2)$.
The exposition in the references above differs from
that of \cite{BCHSY} mostly in the Laurent module $M_L$ it describes. The module which \cite{Bayer-Sturmfels} describes is the $S$-submodule of $k[\ZZ^n]$ generated by the lattice $L$. Whereas the module that these notes call $M_L$ has additional generators.
To obtain the resolution of $\overline R$, \cite{BCHSY} added the vertices given by
the other intersections of the line with the "standard" lattice generated
by the vectors corresponding to $x$ and $y$. Since these intersections do not have integral coordinates, \cite{BCHSY} introduced the idea of taking the ceilings of 
their coordinates. 
If this were a chess game, this move could be marked with "!!".}.
Up to translation by $L$ the coordinate hyperplanes cut $L_\RR$ into four 0-cells $a,b,c,d$ and and four 1-cells $A,B,C,D$ shown in Figure 2.

\goodbreak


Following the general scheme described above we assign weights as follows:
\begin{itemize}
    \item[$\Psi(A)$:] $x^1y^0 = x$
    \item[$\Psi(B)$:] $x^2y^0 = x^2$
    \item[$\Psi(C)$:] $x^2y^{-1} = x^2/y$
    \item[$\Psi(D)$:] $x^3y^{-1} = x^3/y$
    \smallskip
    \item[$\Psi(a)$:] $x^0y^0 = 1$
    \item[$\Psi(b)$:] $x^1y^0 = x$
    \item[$\Psi(c)$:] $x^2y^{-1} = x^2/y$
    \item[$\Psi(d)$:] $x^2y^{-1} = x^2/y$
    \item[$\Psi(e)$:] $x^3y^{-2} = x^3/y^{2}$
\end{itemize}
As in the previous example, the complex $\tilde F$
has just two terms, each an infinite direct sum over the translates by $\ell \in L$
with differential the sum of the translates of
$$
\tilde d = \bordermatrix{
     &A&B&C&D\cr
    a&x&0&0&0\cr
    b&-1&x&0&0\cr
    c&0&-y&1&0\cr
    d&0&0&-1&x\cr
    e&0&0&0&-y
};
$$
\noindent Again, this makes sense because $e$ is a translate of $a$.

\begin{figure}[h]\label{fig:cuspidal cubic 1}
\caption{Diagram for the resolution of the normalization of $k[x,y]/(x^3-y^2)$}
$$
\begin{tikzpicture}[scale=3]
  % Interior vertical grid lines (x=1 and x=2) - black
  \draw (1, 0) -- (1, -2);
  \draw (2, 0) -- (2, -2);

  % Top and bottom horizontal lines - blue
  \draw[blue] (0,  0) -- (3,  0);
  \draw[blue] (0, -2) -- (3, -2);

  % Left and right verticals - red; middle horizontal - black
  \draw[red] (0,  0) -- (0, -2);
  \draw[red] (3,  0) -- (3, -2);
  \draw (0, -1) -- (3, -1);

  % Diagonal line - green
  \draw[green!70!black] (0,0) -- (3,-2);

  % Dots at boundary crossings, labeled a,b,c,d,a (smaller)
  \fill (0,0)    circle (.5pt) node[above left]  {$a:0,0)$};
  \fill (1,-2/3) circle (.5pt) node[above]        {$b$};
  \fill (3/2,-1) circle (.5pt) node[below]        {$c$};
  \fill (2,-4/3) circle (.5pt) node[above]        {$d$};
  \fill (3,-2)   circle (.5pt) node[below right]  {$e:(3,-2)$};

  % Dots at specified x-coordinates, labeled A,B,C,D
  \fill (1/2,-1/3)   circle (1pt) node[below]  {$A$};
  \fill (5/4,-5/6)   circle (1pt) node[above]  {$B$};
  \fill (7/4,-7/6)   circle (1pt) node[below]  {$C$};
  \fill (5/2,-5/3)   circle (1pt) node[below]  {$D$};
\end{tikzpicture}
$$
\end{figure}

The action of $L$ identifies the vertices $a$ and $e$. Thus, modulo the action of $L$ the  differential
of $\FF$ is
$$d: 
\bordermatrix{
     &A&B&C&D\cr
    a&x&0&0&-y\cr
    b&-1&x&0&0\cr
    c&0&-y&1&0\cr
    d&0&0&-1&x\cr    
}.
$$

As before, this quotient can be achived topologically. Again $L_{\RR}$ is a circle, with differential
given by the red arrows drawn inside of the circle
 Figure~\ref{fig:non-normal-hhl-examplex}. \david{I couldn't get this to be 1.4}
 
\begin{figure}[h]
\[
\begin{tikzpicture}
\draw (0,0) circle (2cm);
\fill (270:2cm) circle (2pt) node [below] {$a/e$};
\fill (90:2cm) circle (2pt) node [above] {$c$};
\fill (180:2cm) circle (2pt) node [left] {$b$};
\fill (0:2cm) circle (2pt) node [right] {$d$};

\fill (45:2cm) circle (4pt) node [above right] {$C$};
\fill (135:2cm) circle (4pt) node [above left] {$B$};
\fill (225:2cm) circle (4pt) node [below left] {$A$};
\fill (315:2cm) circle (4pt) node [below right] {$D$};



\draw[->] (50:2.1cm)  arc[radius=2.1cm,start angle=50, delta angle = 25] node[above, midway] {$1$};
\draw[->] (40:2.1cm) arc[radius=2.1cm,start angle=40, delta angle = -25] node[above, midway] {$1$};

\draw[->] (140:2.1cm)  arc[radius=2.1cm,start angle=140, delta angle = 25] node[above, midway] {$x$};
\draw[->] (130:2.1cm) arc[radius=2.1cm,start angle=130, delta angle = -25] node[above, midway] {$y$};

\draw[->] (230:2.1cm)  arc[radius=2.1cm,start angle=230, delta angle = 25] node[below, midway] {$x$};
\draw[->] (220:2.1cm) arc[radius=2.1cm,start angle=220, delta angle = -25] node[below, midway] {$1$};

\draw[->] (320:2.1cm)  arc[radius=2.1cm,start angle=320, delta angle = 25] node[below, midway] {$x$};
\draw[->] (310:2.1cm) arc[radius=2.1cm,start angle=310, delta angle = -25] node[below, midway] {$y$};

\draw[->,red] (140:1.8cm) arc[radius=1.8cm,start angle = 140, delta angle = 115] node[right, midway] {$x^2$};
\draw[->,red] (130:1.8cm) arc[radius=1.8cm,start angle = 130, delta angle = -115] node[below, midway] {$y$};

\draw[->,red] (320:1.8cm) arc[radius=1.8cm,start angle = 320, delta angle = 25] node[above, midway] {$x$};
\draw[->,red] (310:1.8cm) arc[radius=1.8cm,start angle = 310, delta angle = -25] node[above, midway] {$y$};


\end{tikzpicture}
\]
\caption{Diagram for the resolution of the normalization of $k[x,y]/(x^3-y^2)$ as realized on the torus with both non-minimal and minimal differentials indicated.}
\label{fig:non-normal-hhl-examplex}
\end{figure}

This non-minimal matrix is equivalent to the direct sum of the
$2\times 2$ identity matrix and the matrix
$$
d'\ce \begin{pmatrix}
x^2 &-y\\
-y&x
\end{pmatrix}
$$


If we give $x$ and $y$ the natural weights $2$ and 3, then $d'$ is $\ZZ^2/L \cong \ZZ$-homogeneous as a map $S(-4) \oplus S(-3) \to S\oplus S(-1)$,  

Taking the quotient of $\tF$ by $L$ is equivalent to setting the action of a generator $x^{3/y^{2}}$ of $L$ to 1, that
is, to forming $\tF/(1-x^{3}/y^{2)}).$


Since $\tF$ is $\ZZ^{2}$-graded, and the elements 1 and $x^{3}/y^{2}$ have
different $\ZZ^{2}$-degrees, the element $1-x^{3}/y^{2)}$ is a nonzerodivisor on $k[\NN^{2}]$, and thus
the quotient operation preserves exactness.

The determinant of $d$ or $d'$ is 
$(x^3-y^2)$, so the cokernel is annihilated by this element.
%but the cokernel is not $k[x,y]/(x^3-y^2)$!
Since $M_L$ is generated by
$\Psi(p)$, as $p$ runs over the vertices of $L_\RR$, so $M_L/(1-(x^3/y^2))M_L$
is generated by the $\Psi(p)$ for $p$ in the fundamental domain. 
These are the fractions $1,x,x^2/y$, which generate
the fractional ideal $(1, x^2/y) = (1,t)  = \overline R$.

Morever, since $x^3/y = y^2/y = y$ in $R$, we have
$$
(1, x^2/y)*d' = 0
$$
and we see that the cokernel of $d'$ is also isomorphic to 
$R\cdot(x^2/y, y) = R\cdot (x^2/y)$, as required.
\end{example}


\section{Lecture 8 (Ryan Watson): More examples and features}\label{lec:8-HHL-examples}

The resolution constructed in Lecture~\ref{lec:7-HHL-construction} has several important structural features. The first of these is its connection with the Bondal-Thomsen collection. The key case of this is that of the resolution of the torus identity point in $X$. In this case, which corresponds to the case where $L=M_X$, the summands of the resolution $\FF$ are exactly the Bondal-Thomsen elements. In general, we have the following corollary.

\begin{cor}
  \label{cor:hhlSummandsBT}
  Let $X'\subseteq X$ be a toric subvariety of a toric variety and let $L\subseteq \ZZ^n$ be the lattice such that $V(I_L)$ cuts out $X'$ as a subvariety of $X$. Then $L\subseteq M_X\subseteq \ZZ^n$.
  The summands of the resolution $\FF$ are all elements of the Bondal-Thomsen collection. Moreover if $L=M_X$ then the summands of the resolution $\FF$ are exactly the Bondal-Thomsen collection of $X$.
\end{cor}
\begin{proof}
  Every point in $L_{\RR}$ is contained in a cell of the subdivison of $L_{\RR}$, and each cell $A$ of the subdivision
  contributes a single summand to the resolution $\FF$ of the form $S(-\deg(\Psi($A$)))$. 
  Thus the summands that appear in $\FF$ will correspond exactly to the image of $L_{\RR}$ under the composite map
  \[L_{\RR}\xrightarrow{\Psi} \ZZ^n \xrightarrow{-\deg} \Cl(X).\]

  Then observe that the map $\Psi$ factors through $\RR\otimes M_X$ as follows

\[\begin{tikzcd}
  L_{\RR}\arrow[rr,"\Psi"] \arrow[rd,hook]& & \ZZ^n \\
  & \RR\otimes M_X \arrow[ru,"\Psi"]&
\end{tikzcd}\]

This allows us to reduce to the case where $L=M_X$. In that case, we can observe that the composite map $(-\deg)\circ \Psi\circ (-\id)$ gives exactly the map described in Definition~\ref{defn:BTcollection}.
\[-\deg(\Psi(-p)) = -\deg(\prod_{i=1}^n x_i^{\lceil -p_i\rceil}) = -\sum_{i=1}^n\lceil -p_i\rceil D_i=\sum_{i=1}^n\lfloor p_i\rfloor D_i.\]
Since $L_{\RR}$ is a linear subspace of $\RR^n$, the $(-\id)$ in the composite map does not affect the image. Thus the summands of $\FF$ are all Bondal-Thomsen elements and if $L=M_X$, the summands of $\FF$ are exactly the Bondal-Thomsen elements. And as previously noted, in the general case factoring the map through $\RR \otimes M_X$ proves that for any $L\subseteq M_X$ the summands are all Bondal-Thomsen elements.
\end{proof}

\begin{example}
  \label{ex:resHirzebruch3}
  We can illustrate that the summands are Bondal-Thomsen elements in the case of the Hirzebruch by observing that the weights $\Psi$ as a map from $L_{\RR} \rightarrow \ZZ^n$ stratifies $L_{\RR}$ in an $L$-equivariant manner into strata which correspond exactly to the Bondal-Thomsen elements.
  
The diagram has bee labeled with monomials, and each strata colored according to which Bondal-Thomsen element the monomials in that strata correspond to. Each of the 5 Bondal-Thomsen elements gives a strata 
  The cells in this fundamental domain have been colored corresponding to the BT collection elements, which in this case are $\cO_{X}(0,0)$, $\cO_{X}(-1,0)$, $\cO_{X}(2,-1)$, $\cO_{X}(1,-1)$, $\cO_{X}(0,-1)$, $\cO_{X}(-1,-1)$

\begin{figure}
  A single fundamental domain is as follows:
\[
\begin{tikzpicture}[scale=2]
\fill[opacity=0.5, green] (0,2) -- (0,3) -- (3,3) -- cycle;
\fill[opacity=0.5, blue] (0,1) -- (0,2) -- (3,3) -- (3,2) -- (0,1);
\fill[opacity=0.5, red] (0,0) -- (0,1) -- (3,2) -- (3,1) -- (0,0);
\fill[opacity=0.5, brown] (0,0) -- (3,1) -- (3,0) -- (0,0);

\draw[line width=3pt, brown] (0,0) -- (0,1);
\draw[line width=3pt, red] (0,1) -- (0,2);
\draw[line width=3pt, blue] (0,2)-- (0,3);
\draw[line width=3pt, orange] (0,3) -- (3,3);

\draw[line width=3pt, brown] (3,0) -- (3,1);
\draw[line width=3pt, red] (3,1) -- (3,2);
\draw[line width=3pt, blue] (3,2)-- (3,3);


%\draw (3,3) -- (3,0);
\draw[line width=3pt, orange] (3,0) -- (0,0);
\draw[line width=3pt, brown] (0,0) -- (3,1);
\draw[line width=3pt, red] (0,1) -- (3,2);
%\draw (0,1) -- (3,2);
\draw[line width=3pt, blue] (0,2) -- (3,3);
%\draw (0,2) -- (3,3);


%vertices
\node[fill, circle, yellow, inner sep = 4pt] at (0,0) {};
\node[fill, circle, yellow, inner sep = 4pt] at (3,0) {};
\node[fill, circle, yellow, inner sep = 4pt] at (3,3) {};
\node[fill, circle, yellow, inner sep = 4pt] at (0,3) {};
\node at (0,0) {$1$};
\node at (0,1) {$x_2x_3$};
\node at (0,2) {$x_2x_3^2$};
%\node at (0,3) {$x_2x_3^3$};

%horizontal edges
\node at (1.5,0) {$x_1$};

%vertical edges
\node at (0,0.5) {$x_2x_3$};
\node at (0,1.5) {$x_2x_3^2$};
\node at (0,2.5) {$x_2x_3^3$};


%diagonal edges
\node at (1.5,0.5) {$x_1x_2$};
\node at (1.5,1.5) {$x_1x_2x_3$};
\node at (1.5,2.5) {$x_1x_2x_3^2$};

%2-cells
\node at (2,0.25) {$x_1x_2$};
\node at (1.5,1) {$x_1x_2x_3$};
\node at (1.5,2) {$x_1x_2x_3^2$};
\node at (1,2.75) {$x_1x_2x_3^3$};

\matrix[draw] at (4,2) {
  \node[fill=yellow,inner sep = 2pt] {}; & \node {$\cO_{X}(0,0)$};\\
  \node[fill=orange,inner sep = 2pt] {}; & \node {$\cO_{X}(-1,0)$};\\
  \node[fill=brown,inner sep = 2pt] {}; & \node {$\cO_{X}(2,-1)$};\\
  \node[fill=red,inner sep = 2pt] {}; & \node {$\cO_{X}(1,-1)$};\\
  \node[fill=blue,inner sep = 2pt] {}; & \node {$\cO_{X}(0,-1)$};\\
  \node[fill=green,inner sep = 2pt] {}; & \node {$\cO_{X}(-1,-1)$};\\
};

\end{tikzpicture}
\]
\caption{A diagram of the stratificaton on a single fundametal domain for the 3rd Hirzebruch. \jay{This needs better colors, possibly also offset the strata to make them look more obviously separated}}
\label{fig:hirzebruch-stratification}
\end{figure}

\end{example}

There is one other important structural feature of these resolutions, which is that they depend only on the rays of the toric variety $X$ and the lattice $L$ and are independent of the fan structure $\Sigma_X$. Or equivalently, one may say that the resolution depends only on the graded Cox ring $S$ and the toric ideal $I_L\subseteq S$ and is independent of the choice of irrelevant ideal. One important case of this we highlight in the following corollary.

\begin{cor}
\label{cor:diagonalUniform}
    Assume that $X$ and $X'$ are smooth, projective toric varieties with the same Cox ring $S$.  Then, as free complexes of $S\otimes_k S$-modules, the following are all the same:
    \begin{enumerate}
        \item The resolution of the diagonal $X\subseteq X\times X$.
        \item The resolution of the diagonal $X'\subseteq X'\times X'$.
        \item  The resolution of the closure of the graph $\Gamma \subseteq X\times X'$ of the birational map $X\dashrightarrow X'$.
    \end{enumerate}
\end{cor}
\begin{proof}
  Proof 1:  The construction of the HHL resolution only depends on the rays of the product and the lattice determining the diagonal. So if you do the construction in any of these cases, it is literally exactly the same.

    Proof 2:  Write $I_\Delta\subseteq S\otimes_k S$ for the defining ideal of the diagonal $X\subseteq X\times X$.  Write  Write $I_{\Delta'}\subseteq S\otimes_k S$ for the defining ideal of the diagonal $X'\subseteq X'\times X'$.  And write $I_\Gamma\subseteq S\otimes_kS$ for the defining ideal of $\Gamma\subseteq X\times X'$.  These three ideals are all multigraded, prime ideals on $S\otimes_k S$ whose vanishing locus contains the dense torus, and thus the ideals are all equal.  The three HHL resolutions are, up to homotopy, the minimal free resolutions of the normalizations of $S\otimes_k S/I_{\Delta}$, $S\otimes_k S/I_{\Delta'}$, and $S\otimes_k S/I_{\Gamma}$ respectively.  But since these modules are all equal, so are their minimal free resolutions. \jay{Do we want to keep both proofs?}
\end{proof}



This is connected of the independence of the Bondal-Thomsen collection from the fan structure as noted after Definition~\ref{defn:BTcollection}. However, a priori, one may be surprised that the resolution does not depend on the toric variety $X$. For instance, it is certainly not the case that simply translating any resolution by line bundles by pushforward along birational maps from one part of the secondary fan to another should yield a resolution!

This uniformity is a first clue that these resolutions are pointing towards a uniformity across all toric varieties with the same Cox ring. This uniformity forms the starting point for the description of the Cox category that is explored starting from Lecture~\ref{lec:12-DCox-definition}.


%% Discussion of how this is kind of surprising!!  There was, a priori, no reason to believe that the ``best'' toric analogue of Beilinson's resolution  would only involve the Cox ring (i.e. that it would not depend on the irrelevant ideal whatsoever).  This is a first clue that these resolutions are pointing towards some sort of uniformity for all of the toric varieties with the same Cox ring.  That uniformity will be explored in more depth in later lectures.

One specific case where the correspondence between the BT collection and the summands of the resolution is of particular importance is the diagonal. The summands of the diagonal will all be of the form $O_X(D)\boxtimes O_X(D')$ for pairs of Bondal-Thomsen elements. Some care is require though, as not every pair of Bondal-Thomsen elements will appear.

\begin{cor}
  \label{cor:diagonal-BTcollection}
  The line bundles appearing the resolution of the diagonal $\FF$ arising from HHL are of the form $O_X(D)\boxtimes O_X(D')$ for some $D$,$D'$ in the Bondal-Thomsen collection. Moreover every element of the Bondal-Thomsen collection appears both on both the right and left hand side of $O_X(D)\boxtimes O_X(D')$.
\end{cor}
\begin{proof}
  Observe that the lattice $L$ for the diagonal is the Lawrence lift of $M_X$, that is the lattice
  \[L := \{(\mathbf{v},-\mathbf{v}) \in \ZZ^{2n} \,|\, \mathbf{v}\in M_X\}.\]
  Thus the line bundles that appear in the resolution of the diagonal are of the form $O_{X\times X}(-\lceil (\mathbf{p},-\mathbf{p})\rceil)$ for $p$ a point in $\RR \otimes M_X$ which can then be expanded as follows:
  \[O_{X\times X}(-\lceil (\mathbf{p},-\mathbf{p})\rceil)=O_X(-\lceil v\rceil)\boxtimes O_X(\lfloor v\rfloor).\]
  The left hand side of this summand is $O_X(D)$ for some $D$ in the BT collection by the same reason as in Corollary~\ref{cor:hhlSummandsBT}. And $O_X(\lfloor v\rfloor)$ is quite directly the generator of the BT collection associated to $v$. Finally, as $v$ varies over all points in $\RR \otimes M_X$, every Bondal-Thomsen element appears as by Definition~\ref{defn:BTCollection}.
\end{proof}

The Fourier-Mukai transform, which forms a key step in the proof of Conjecture~\cite{conj:BES}, results in a complex whose summands will be drawn from the left hand side of the summands of the diagonal. Consequently, the complexes that result from applying the Fourier-Mukai transform to give monads for arbitrary coherent sheaves will result in complexes whose summands are all Bondal-Thomsen elements. This gives rise to the following corollary.

\begin{cor}
  If $\mathcal{F}$ is a coherent sheaf on $\mathcal{L}$, then it is resolved by a monad containing as summands only Bondal-Thomsen elements.
\end{cor}
\begin{proof}
  This is a consequence of applying the Fourier-Mukai and Corollary~\ref{cor:diagonal-BTcollection}.
\end{proof}

We conclude with the resolution of the diagonal for the third Hirzebruch surface. We also remark that the resolutions constructed for the diagonal are always minimal, a feature that does not hold for general $L$.

\begin{example}
  Let $X=\cH_3$, and let $S$ be the Cox ring of $X\times X$. Then each summand is of the form $S((-\deg(\Psi(A)),-\deg(\Psi(-A))))$. For example, for the summand that corresponds to the bottom right triangle of Figure~\ref{fig:hirzebruch-stratification}, $-\deg(\Psi(A))$ which corresponds to the Bondal-Thomsen element $O_X(2,-1)$. The cell $-A$ is equivalent after a translation by an element of $L$ to the top left triangle in the diagram, corresponds to the Bondal-Thomsen element $O_X(-1,-1)$. This gives the summand $S(-2,-1,-1,-1)$.

  Repeating this construction for every cell will give all summands of the resolution of the diagonal.
  \[
   \FF : \begin{matrix}
    S(0,0,0,0)\\
    \oplus\\
    S(2,-1,1,-1)\\
    \oplus\\
    S(1,-1,2,-1)\\
  \end{matrix}\longleftarrow
  \begin{matrix}
    S(-1,0,-1,0)\\
    \oplus\\
    S(2,-1,0,-1)^2\\
    \oplus\\
    S(1,-1,1,-1)^2\\
    \oplus\\
    S(0,-1,2,-1)^2\\
  \end{matrix}
  \longleftarrow
  \begin{matrix}
    S(-2,-1,-1,-1)\\
    \oplus\\
    S(1,-1,0,-1)\\
    \oplus\\
    S(0,-1,1,-1)\\
    \oplus\\
    S(-1,-1,2,-1)\\
  \end{matrix}
  \longleftarrow 0
  \]
  \jay{Question: should we just use box products for this? It might look more like Bellinson's resolution then}
\end{example}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 9 (Greg Smith): The proof}\label{lec:9-HHL-proof}
The goal of this section is to prove:

\begin{theorem} \cite{HHL}\label{thm:HHL-resolution}
With notation as in Section 7, the complexes $\tF$ and $\FF$ are $S$-free resolutions of $M_{L}$ and $\overline{S/I_{L}}$, respectively. 
\end{theorem}

The original proof of the Hanlon-Hicks-Lazarev Theorem in~\cite{HHL} is fairly technical.  However, two recent preprints have dramatically simplified the proof.  The preprint~\cite{BCHSY} (see in particular Proposition 3.2) relates the Hanlon-Hicks-Lazarev construction to a more classical algebraic construction involving binomial ideals, and provides an elementary and purely algebraic proof of the main result, as well as broad generalization of those results.  The preprint~\cite{BH25} utilizes a similar basic idea as~\cite{BCHSY}, but provides a terser and narrower proof.

Before diving into the proofs of the main theorem, it is important to carefully describe more carefully how the complexes $\tilde \FF$ and $\FF$ are related to each other and in particular provide a careful definition of the complex $\FF$.
The first step of this is to observe that as $\tilde \FF$ is $L$-equivariant, it acquires the structure of an $S[L]$-module. $S[L]$ can be presented explicitly as follows
\[S[L]=S\cdot \{z^{\mathbf{u}} \,|\, \mathbf{u}\in L\}\subseteq S[z_1^{\pm},\ldots,z_n^{\pm}]\]
$M_L$ also acquires the structure of an $S[L]$-module, where $z^{\mathbf{u}}$ acts on a monomial $x^{\mathbf{v}}\in M_L$ by sending it to $x^{\mathbf{v}+\mathbf{u}}$. It is worth observing that this makes $M_L$ into a finitely generated $S[L]$-module so long as $L\cap \NN^n=\{0\}$. It is not hard to show that the $S[L]$-module structure on $M_L$ and on $\tilde \FF$ are compatible.

Then $S$ can also be given an $S[L]$-module structure under the quotient by the ideal $\langle z^{u}-1 \,|\, u\in L\rangle$. Observe that for any choice of basis $u_1,\ldots,u_r\in L$, the sequence $z^{u_1}-1,\ldots,z^{u_r}-1$ forms a regular sequence for $S[L]$ and also of the module $M_L$. Then $\FF$ can be obtained from $\tilde \FF$ by the quotient by such a regular sequence, or equivalently, $\FF = \tilde \FF \otimes_{S[L]} S$.

Regardless of the exact approach, a key observation is that the strands of the complex $\FF$ in a fixed degree $\alpha\in \ZZ^n/L$ is equal to the strands $\FF_{\mathbf{u}}$ for any $\mathbf{u}\in \alpha$. Additionally  and also equal to the can be given in terms of the cellular chain complex of a space. In particular, we can define the subset given by
\[(L_{\RR})_{\leq \mathbf{u}}:= \{p\in L_{\RR} \,|\, \Psi(p)\text{ divides }x^{\mathbf{u}}\} = \{p\in L_{\RR} \,|\, \lceil p_i\rceil \leq u_i\text{ for all } i=1,\ldots,n\}\]
Then the cellular chain complex of this subcomplex of $L_{\RR}$ is identical to the strand of $\FF$ in degree $\alpha$. Then this following proposition is based primarily on the proof of Proposition~2.13 and the alternate sketch of proof of Corollary~2.15 from \cite{BCHSY} and is similar the proof of Proposition~2.6 from \cite{BH25}.

\begin{prop}[\cite{BCHSY,BH25}]
  \label{prop:hhlStrands}
  For $\mathbf{u}\in \ZZ^n$, an element of the class $\alpha\in \ZZ^n/L$, the complexes of $k$-vector spaces $\FF_{\alpha}$, $\tilde \FF_{\mathbf{u}}$ and $C_\bullet(L_{\RR})_{\leq \mathbf{u}};k)$ are isomorphic.
\end{prop}
\begin{proof}
  Interpreting $\FF$ as $\tilde \FF \otimes_{S[L]}S$ there is a map $\tilde \FF \rightarrow \FF$ by $-\otimes_{S[L]}1$. For any cell $A\subseteq L_{\RR}$, the map on the summand of $\tilde \FF$ simply is the identity map $S(-\Psi(A))\rightarrow S(-\deg(\Psi(A)))$ which coarsens the grading from $\ZZ^n$ to $\ZZ^n/L$.

  Then the image of the degree $\mathbf{u}$ component of the above is simply the map to the subspace of $S(-\deg(\Psi(A))$ spanned by the monomial $x^{\mathbf{u}-\Psi(A)}$, or zero if the monomial is a Laurent monomial.
  Then by varying the $L$-translate $A'$ of $A$, one gets all monomials of $S(-\deg(\Psi(A))$ of the form $x^{\mathbf{u}-\Psi(A)}$, which is a basis for the degree $\alpha$ elements of $S(-\deg(\Psi(A)))$. Applying this across all cells of $L_{\RR}/L$, one finds that the restricted map $\tilde \FF_{\mathbf{u}}\rightarrow \FF_{\alpha}$ is an isomorphism of complexes of k-vector spaces.
  
  Now to relate to the cellular homology, observe that For each cell $A\subseteq L_{\RR}$ the summand of $A$ in $\tilde \FF$ has component in degree $\mathbf{u}$ given by

  \[S(-\Psi(\mathbf{p}))_{\mathbf{u}} = 
  \begin{cases}
    k & \Psi(\mathbf{p})\text{ divides } x^{\mathbf{u}}\\
    0 & \text{otherwise}
  \end{cases}\]

  Thus the cells of $L_{\RR}$ for which the summand corresponding to $A$ participates is exactly those cells contained in $(L_{\RR})_{\leq \mathbf{u}}$. Moreover, the maps between these summands are exactly the differentials from the cellular structure, so we have
  \[\tilde \FF_{\mathbf{u}} = C_i((L_{\RR})_{\leq u};k)\]
\end{proof}

That $\FF$ is a resolution is then immediate, as the subcomplex $(L_{\RR})_{\leq \mathbf{u}}$ are polyhedral and thus contractable or empty. As a consequence, the only homology is in $H_0$.

The second key is to prove that the module is the integral closure $\overline{S/I_L}$. Here we recall a fact about toric rings. First the ring $S/I_L$ is a semigroup ring for the semigroup $A=\NN^n/L$, that is the image of $\NN^n$ under the map $\ZZ^n \rightarrow \ZZ^n/L$. Then for a semigroup ring $k[A]$, the integral closure is itself a semigroup ring, and is in fact the semigroup ring of the saturation $\overline{A}$.

The saturation affine semigroup $A\subseteq \ZZ^n$ is given by
\[\overline{A} := (\RR_{\geq 0}A)\cap \ZZ^n \]

There are then two plausible approaches to proving this, which correspond to the approaches from \cite{BCHSY} and \cite{BH25} respectively. One can either prove that the generators of the module $M_L$ correspond to monomials in $k[\ZZ^n]$ which generate $\overline{A}$ as a $A$-module. Or one can prove that the those degrees $\alpha\in \ZZ^n/L$ where $(L_{\RR})_{\leq u}$ is non-empty are exactly the degrees of $A$. The approach taken here follows mostly the approach in Proposition~3.3 of \cite{BCHSY}. The corresponding result in \cite{BH25} is Lemma~2.8.

\begin{prop}[TODO cite both]
  \label{prop:resolves-integral-closure}
  $M_L \otimes_{S[L]} S$ is isomorphic to $\overline{S/I_L}$ as an $S$-module.
\end{prop}
\begin{proof}
  $M_L\otimes_{S[L]} S$ is generated by monomials in $k[\ZZ^n/L]$ of the form $x^{\lceil \textbf{v}\rceil}$ for $\textbf{v}$ a vertex of the cellular structure on $L_{\RR}$\jay{TODO technically this needs the regular sequence statement/the exactness of the functor}. And the normalization viewed as the semigroup ring $k[\overline{A}]$ is naturally a $S$-submodule of $k[\ZZ^n/L]$. So we will show that they are identical as submodules.

  First we show that the monomials $x^{\lceil \textbf{v}\rceil}$ are elements of the semigroup $\overline{A}$.
  Let $\eta:\ZZ^n\rightarrow \ZZ^n/L$ be the usual quotient map and $\eta_{\RR}:\RR^n\rightarrow \RR^n/L$ the corresponding map after tensor with $\RR$. For a vertex $\mathbf{p}\in L_{\RR}$, we have
  \[\eta(\lceil \mathbf{p}\rceil) = \eta(\lceil \mathbf{p}\rceil)-\eta(\mathbf{p}) = \eta(\lceil \mathbf{p}\rceil - \mathbf{p})\]
  However $\lceil \mathbf{p}\rceil - \mathbf{p}$ has all positive coordinates and so is in $\RR_{\geq 0} A=\eta(\RR_{\geq 0}^n)$.

  For the converse, suppose that $\mathbf{a}\in \overline{A}$, then
  we wish to show that the corresponding element of $k[\overline{A}]$ is an element of $M_L\otimes_{S[L]} S$.
  As $a\in \overline{A} = \eta(\RR_{\geq 0}^n)\cap (\ZZ^n/L)$, there exists
  $\mathbf{q}\in \RR_{\geq 0}^n$ and $\mathbf{u}\in \ZZ^n$ such that
  \[\mathbf{a} = \eta_{\RR}(\mathbf{q}) = \eta(\mathbf{u})\]

  It suffices to prove there exists a vertex $p'\in L_{\RR}$ such that $\Psi(p')$ divides $x^{\mathbf{u}}$.
  Let $\mathbf{p}=\mathbf{u}-\mathbf{q}$, then as $\lceil \mathbf{p} \rceil = \mathbf{u} - \lfloor \mathbf{q}\rfloor$ and thus $\Psi(\mathbf{p})$ divides $x^{\mathbf{u}}$. To get a vertex, observe that if $\mathbf{p}'$ is any vertex of the unique cell of $L_{\RR}$ that contains $\mathbf{p}$ in it's relative interior, then $\Psi(\mathbf{p}')$ divides $\Psi(\mathbf{p})$ and thus divides $x^{\mathbf{u}}$ as desired.
\end{proof}

\begin{remark}
  While the generators of $M_L$ are phrased in terms of the vertices of the cell structure on $L_{\RR}$, a (more redundant) set of generators can be given by simply taking $x^{\lceil\mathbf{p} \rceil}$ for all points $p\in L_{\RR}$. One observation from this is that while the resolution depends on the cell structure, the module $M_L$ only depends on the lattice $L$ (and our use of the ceiling function).
  \jay{TODO move this to section 7}
\end{remark}

Together these two propositions prove Theorem~\ref{thm:HHL-resolution}

\begin{proof}[Proof of Theorem~\ref{thm:HHL-resolution}]
  That the complexes $\tilde \FF$ and $\FF$ are resolutions follows from Proposition~\ref{} by observing that $(L_{\RR})_{\leq \mathbf{u}}$ is polyhedral and thus either contractable or empty.

  That the complex $\tilde \FF$ resolves $M_L$ follows first by observing that there exists a canonical $\ZZ^n$-graded map $\FF_0\rightarrow k[\ZZ^n]$ compatible with the resolution thus giving a $\ZZ^n$-graded map $H_0(\tilde FF)\rightarrow k[\ZZ^n]$.
  To show that $H_0(\tilde \FF)\cong M_L$, observe first that for a degree $\mathbf{u}\in \ZZ^n$,
  $H_0(\tilde \FF)_{\mathbf{u}}=H_0((L_{\RR})_{\leq \mathbf{u}})$. Moreover $(L_{\RR})_{\leq \mathbf{u}}$ is either contractable if there exists a vertex $\mathbf{v}\in L_{\RR}$ such that $\Phi(\mathbf{v})$ divides $x^{\mathbf{u}}$ or empty otherwise. As $M_L$ is generated by the vertices $\mathbf{v}\in L_{\RR}$, it follows that $(L_{\RR})_{\leq \mathbf{u}}$ is contractable if and only if $x^{\mathbf{u}}\in M_L$ and empty otherwise.

  That the complex $\FF$ resolves $\overline{S/I_L}$ follows from Proposition~\ref{prop:resolves-integral-closure}.
\end{proof}

\ifdefined\whole
\else
\bibliographystyle{plain}
\bibliography{Bibliography}
\end{document}
\fi
