%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifdefined\whole
\else
\documentclass{article}
\input{preamble}
%\begin{document}
\fi

\section{Lecture 11 (Lauren Cranton Heller): The secondary fan}\label{lec:11-secondary-fan}
In this section, we define the Cox category of a toric variety and explain how it combines the sheaf categories of all of the toric varieties associated to a given multigraded Cox ring.

\subsection{Toric varieties of a multigraded ring}
Distinct smooth projective toric varieties can have the same Cox ring with the same grading, adding a wrinkle to generalizations of the dictionary between projective space and the standard graded polynomial ring.  The various possibilities are parametrized by what is called the \defi{secondary fan} or \defi{GKZ fan} of the toric variety, and the goal of this subsection is to provide a crash course in how to think about this fan.

We start with a polynomial ring $k[x_1,\ldots,x_n]$ and a map $\deg\colon\ZZ^n\to\Cl(S)$ to a finitely generated abelian group $\Cl(S)$, which induces a $\Cl(S)$-grading on $S$.  We will assume throughout that this grading satisfies the hypotheses of Proposition~\ref{prop:goodMultigradings}, ensuring that there exists \emph{some} simplicial projective toric variety with $S$ as its Cox ring.  Equivalently one may start with one such variety to obtain a suitable multigraded ring.

Write $M$ for the kernel of $\deg$, a lattice in $\ZZ^n$, and $G$ for the algebraic group $\Spec k[\Cl(S)]$, so that there is a short exact sequence

\begin{align}\label{eq:M-SES}
  0\to M\to\ZZ^n\to\Cl(S)\to 0.
\end{align}

\lauren{something about Gale duality}

\lauren{put setup in labeled environment for reference}

The crucial observation of the secondary fan is that there are only finitely many toric varieties arising from $S$, and in fact that they can be arranged into a polyhedral structure which reflects their geometry.  The finitely many possibilities can be enumerated in several different ways, which we will address in turn through the subsequent subsections.
\begin{description}
  \item[GIT quotient/ample divisor]  In \lauren{reference} we saw that a smooth projective toric variety is a GIT quotient.  The \lauren{geometric??} quotients are parametrized by linearized line bundles.  Choosing a linearization means choosing a divisor to be ample on the quotient, and we will see that the chambers of the secondary fan are in a sense possible nef cones.
  \item[polytope/simplicial fan]  If a projective toric variety has $S$ as its multigraded Cox ring then we also know that its rays must come from \eqref{eq:M-SES}.  The collection of polytopes with normal vectors in a fixed list forms a fan, whose cones will exactly enumerate the possible simplicial fans on subsets of the rays. \lauren{how does simplicial come in?}
  \item[irrelevant ideal]  Perhaps the simplest way to describe which toric varieties are possible is to describe their irrelevant ideals, since $S$ with its grading and a suitable irrelevant ideal fully determines a toric variety.  Indeed the set of such ideals is easy to describe in terms of the map $\deg$, and each ideal quickly determines both pieces of data above.
\end{description}

A reader primarily concerned with computation could start with Section~\ref{sec:irrelevant-ideals} and take on faith that the ideals describe there correspond to valid quotients and form a fan.  Here we give an example of all three perspectives for our favorite toric variety.

\lauren{examples moved here from previous version}

\begin{example}\label{ex:hirzsecondary}
  Let us consider the example of $\mathcal H_3$, the Hirzebruch surface of type $3$.  The Cox ring is~$S=\CC[x_0,x_1,x_2,x_3]$, and the degrees of the variables are $(1,0), (-3,1), (1,0)$ and $(0,1)$, respectively.    First consider the monomial $x_0^2x_1^3$.  This monomial spans any $d\in \Cl(S)\otimes \QQ$ that lies in the span of $\deg_{\QQ}(x_0^2) = (2,0)$ and $\deg_{\QQ}(x_1^3) = (-9,3)$, i.e. this monomial spans the entire effective cone (see graphic). Consider the squarefree monomial ideals $B_1 = \langle x_0x_1, x_1x_2, x_1x_3\rangle$ and~$B_2 = \langle x_0x_1,x_0x_3, x_1x_2,x_2x_3\rangle$.  We have that $\Gamma_1 = \text{cone}(B_1)$ is the interior of the cone spanned by $(-3,1)$ and $(0,1)$, while $\Gamma_2 = \text{cone}(B_2)$ is the interior of the cone spanned by $(0,1)$ and $(1,0)$.

  \begin{center}
    \begin{tikzpicture}[scale=2]

      \def\axlim{1.6}

      \begin{scope}
        \clip (-\axlim,-\axlim) rectangle (\axlim,\axlim);

        % Cone region (left): x<=0 and y >= -x/3
        \fill[orange!35]
        (0,0)
        -- (0, \axlim)
        -- (-\axlim, \axlim)
        -- (-\axlim, {1/3*\axlim})
        -- cycle;

        % Positive quadrant (right)
        \fill[blue!20]
        (0,0) rectangle (\axlim, \axlim);
      \end{scope}

      % Draw only the negative x-axis and negative y-axis as solid
      \draw[->, thick] (-\axlim, 0) -- (0, 0);
      \draw[->, thick] (0, -\axlim) -- (0, 0);

      % Positive x-axis and positive y-axis as dotted boundary rays
      \draw[black, thick, dotted, ->, shorten >=2pt] (0,0) -- (\axlim, 0);
      \draw[black, thick, dotted, ->, shorten >=2pt] (0,0) -- (0, \axlim);

      % Tick marks
      \foreach \x in {-1, 1} {
        \draw (\x, 2pt) -- (\x, -2pt) node[below, font=\small] {$\x$};
      }
      \foreach \y in {-1, 1} {
        \draw (2pt, \y) -- (-2pt, \y) node[left, font=\small] {$\y$};
      }

      % Left boundary ray of cone: direction (-3,1), dotted
      \draw[black, thick, dotted, ->, shorten >=2pt]
      (0,0) -- ({-3/sqrt(10)*\axlim*1.05}, {1/sqrt(10)*\axlim*1.05})
      node[left, font=\small] {$(-3,1)$};

      % Label (0,1) placed to the right of the y-axis, clear of shading
      \node[font=\small] at (0.22, \axlim*0.92) {$(0,1)$};

      % Labels centered in each shaded region
      \node[orange!70!black] at ({-\axlim/2}, {\axlim/2}) {$\Gamma_1$};
      \node[blue!60!black]   at ({ \axlim/2}, {\axlim/2}) {$\Gamma_2$};

      % Origin dot
      \filldraw (0,0) circle (1pt);

    \end{tikzpicture}
  \end{center}
\end{example}

\begin{example}\label{ex:hirzSecondary2}
  We return to Example~\ref{ex:hirzsecondary}. The ideal $B_2$ is the irrelevant ideal of the Hirzebruch surface~$\mathcal{H}_3$, so the chamber $\Gamma_2$ corresponds to $\mathcal{H}_3$. The chamber $\Gamma_1$ corresponds to the weighted projective space $\PP(1,1,3)$; one way to see this is to apply Theorem~\ref{thm:mainsecondary}(4) with $a = (-1, 1)$, and notice there is an isomorphism of $\Z$-graded rings $S_a \cong \k[y_0, y_1, y_2]$, where $\deg(y_0) = \deg(y_1) = 1$, and $\deg(y_2) = 3$. These two cases demonstrate notably different behavior.  For $\mathcal H_3$, we have that~$\Cl(\mathcal H_3)=\ZZ^2 = \Cl(S)$, and hence we have not contracted any divisors.  In this case, {\color{red} $\Gamma_2$} is precisely the ample cone of $\mathcal H_3$.
  Things are more complicated for $\PP(1,1,3)$, as the presentation of $\PP(1,1,3)$ is nonstandard.  The Cox ring of $\PP(1,1,3)$ involves only 3 variables, but we have $S=\CC[x_0, x_1, x_2, x_3]$.  This is because the ray $\rho_1$ is not utilized in the fan corresponding to $\PP(1,1,3)$.  At the algebraic level, the corresponding variables determines a principal component of the irrelevant ideal, as we have $B_1 = \langle x_1\rangle \cap \langle x_0,x_2,x_3\rangle$.  There is still a natural map~$\Phi\colon \ZZ^2 = \Cl(S) \to \Cl(\PP(1,1,3))$; it must have $\deg(x_1)$ in its kernel, i.e. it must be the map $\Phi(a,b) = a +3b$. Under this map, every element $\Phi(\Gamma_1)$ covers the ample cone of $\PP(1,1,3)$.  However, there are elements outside of $\Gamma_1$ that also map to ample divisors under this map.
\end{example}

\subsection{GIT quotients}\label{sec:variation-of-GIT}
The sequence \eqref{eq:M-SES} induces maps of algebraic groups
\[0\gets \Spec k[M]\gets (k^*)^n\gets G\gets 0.\]  The group $(k^*)^n$ acts on the affine space $\Spec S$ by componentwise multiplication so $G$ does as well.  (Note that we have fixed a basis for $\ZZ^n$ by choosing variables for $S$.)

We will consider the quotient of $\Spec S$ by the action of $G$, which depends on a choice of linearized line bundle on $\Spec S$.  We briefly recall some relevant terminology from geometric invariant theory (GIT).  The case of torus actions on affine spaces is much simpler than the general theory.  \lauren{give citation for additional reading}

\begin{defn}
  A \emph{$G$-linearized line bundle} on a space $X$ with a $G$ action is a line bundle $\cL$ on $X$ with an action of $G$ compatible with the action on $X$ \lauren{write out?} such that the zero section of $\cL$ is $G$-invariant.  The \emph{$G$-equivariant Picard group} of $X$ is the group of $G$-linearized line bundles under tensor product, up to $G$-equivariant isomorphism. \lauren{for people who know more about GIT: am I using these words correctly?}
\end{defn}

Since $\Spec S$ is affine, it only has the trivial line bundle $\cO$.  Actions of $G$ on $\cO$ are given by elements of $\Cl(S)$.

\begin{prop}\label{prop:eq-Picard-gp}
  In the setup above $\Cl(S)$ is the $G$-equivariant Picard group of $\Spec S$.
\end{prop}

\begin{proof}
  An action of $G$ on $\cO$, the only isomorphism class of line bundle on $\Spec S$, is given by a character $\chi\colon G\to\CC^*$. \lauren{why does this agree with linear equivalence?} The element $g\in G$ then acts on fibers of $\cO$ by multiplication with $\chi(g)$.  By definition of $G$ the character $\chi$ is given by a map $\chi^\sharp\colon \CC[t^{\pm 1}]\to\CC[\Cl(S)]$ so that $\chi$ is a morphism of algebraic groups, and these are determined by the image $\chi^\sharp(t)$ in $\Cl(S)$.  \lauren{explain why it can't have a coefficient}

  Tensor product of $G$-linearized line bundles corresponds to multiplication of characters and addition of elements in $\Cl(S)$.
\end{proof}

By Proposition~\ref{prop:eq-Picard-gp} and \lauren{general GIT theorem}, the possible quotients of $\Spec S$ by $G$ are parametrized by elements $d\in\Cl(S)$.  Since $\Spec S$ had an action of $(k^*)^n$ the quotients retain an action of $\Spec k[M]$, which is a torus. \lauren{elaborate?} In fact they are toric varieties, as we will see later by assigning them to fans.

According to GIT, in order to construct good quotients we must first remove the unstable locus in $\Spec S$ corresponding to $d$.  The quotient of the remaining semistable locus is then isomorphic to
\[\Proj\bigoplus_{i\in\NN}\Gamma(\Spec S,\cL_d^{\otimes i})^G\]
where $\cL_p$ is the $G$-linearized line bundle of $d\in\Cl(S)$ and multiplication in the ring is given by tensor product of sections. \lauren{cite} In the toric case these equivariant sections are elements of $S$.
\begin{lemma}
  With $\cL_d$ the line bundle on $\Spec S$ given by Proposition~\ref{prop:eq-Picard-gp} for $d\in\Cl(S)$, we have that $\Gamma(\Spec S,\cL_d)^G=S_d$.
\end{lemma}
\begin{proof}
  \lauren{..}
\end{proof}
Write $S_{\NN d}$ for the subring of $S$ consisting of polynomials with degrees in the set $\NN d$.

\begin{cor}\label{cor:quotient-Proj}
  The GIT quotients of $\Spec S$ by $G$ are of the form $X_d=\Proj S_{\NN d}$ for $d\in\Cl(S)$. \lauren{defeq?}
\end{cor}

%Given $d\in\Cl(S)$, write $X_d$ for the toric variety $\Proj S_{\NN d}$.
We will see more concrete constructions of these spaces in the next subsection, along with descriptions of the semistable and stable loci.

\subsection{Polytopes and the combinatorial secondary fan}\label{sec:polytope-fan}
The toric structure of the quotients $X_d$ connects their GIT problem to the combinatorial literature about the secondary fan.  (See, for instance, \cite{OdaPark21}.)  In this context the secondary fan parametrizes polytopes whose normal vectors lie in a fixed list.

\begin{defn}
  Given $\alpha\in\QQ^n$, write $P_\alpha$ for the polytope in $M\otimes_\ZZ\QQ$ defined by the restriction of the facets $x_i\geq -\alpha_i$ for all $i$.
\end{defn}

\begin{example}
  \lauren{restriction process}
\end{example}

Note that the normal vectors of the polytope $P_\alpha$ lie in the list $\nu_1,\ldots,\nu_n$.  However not all $n$ inequalities/normal vectors need be required, if some of the hyperplanes $x_i=-\alpha_i$ do not intersect $P_\alpha$ in a facet (or at all).  \lauren{CLS} refer to these as ``virtual'' facets.  Replacing~$\alpha$ with another vector of the same degree only translates the polytope.

\begin{lemma}[\lauren{cite CLS}]
  If $\alpha,\alpha'\in\ZZ^d$ have $\deg\alpha=\deg\alpha'$ then $P_{\alpha'}=m+P_\alpha$ for some $m\in M$. \lauren{does this work for rational $\alpha?$}
\end{lemma}

Hence $P_\alpha$ is determined by elements of $\Cl(S)\otimes_\ZZ\QQ$ up to translation within $M\otimes_\ZZ\QQ$.  At certain degrees the face structure may change---for instance when a collection of hyperplanes intersects in unexpected codimension.

\begin{example}\label{ex:secondary-wall}
  \lauren{polytope along a wall}
\end{example}

This behavior cannot occur for a general choice of $\alpha$, creating a polyhedral fan in the space of polytopes.  The interiors of top dimensional cones collect all degrees in $\Cl(S)\otimes_\ZZ\QQ$ whose polytopes share a normal fan.  To describe lower dimensional cones we additionally specify for which indices~$i$ the hyperplanes $x_i=-\alpha_i$ do not intersect $P_\alpha$, in order to distinguish cases like Example~\ref{ex:secondary-wall}.

Let $\Sigma$ be a generalized fan in $N\otimes_\ZZ\QQ$ with rays among the vectors $\nu_1,\ldots,\nu_n$ and $F$ a subset of the indices $1,\ldots,n$ of the $\nu_i$ \emph{not} appearing in $\Sigma$.  \lauren{give pair for example}  Define $\tilde\Gamma(\Sigma,F)$ to be the set of $\alpha\in\QQ^n$ such that there exists a convex support function $\varphi$ on $\Sigma$ with $\varphi(\nu_i)=-\alpha_i$ for all $i\notin F$ and $\varphi(\nu_i)\geq-\alpha_i$ for all $i\in F$ \lauren{define $\nu_i$ from Gale dual}.

Compared to ordinary fans of toric varieties, generalized fans may contain cones which are not strongly convex.  \lauren{cite CLS}  As with the behavior from Example~\ref{ex:secondary-wall}, this does not occur for a general choice of $\alpha$, and we will focus on the general (not generalized!) case. \lauren{make and reference remark about walls}

\begin{lemma}\label{lem:GKZ-def}
  Let $\alpha\in\QQ^n$ such that $\dim P_\alpha=n$ and the normal vectors of $P_\alpha$ are exactly $\{\nu_i:i\in G\}$ for $G\subseteq\{1,\ldots,n\}$.  Then $\alpha\in\tilde\Gamma(\Sigma,F)$ where $\Sigma$ is the normal fan of $P_\alpha$ and $F$ is the complement of $G$.
\end{lemma}

\begin{proof}
  Let $X_\alpha$ be the toric variety of the polytope $P_\alpha$.  By \cite[Proposition~6.1.10]{CLS} the divisor $\sum_{i\in G}\alpha_iD_i$ \lauren{notation?} is ample on $X_\alpha$, so by \cite[Theorem~6.1.14]{CLS} it has a strongly convex support function $\varphi$ on $\Sigma$, satisfying $\varphi(\nu_i)=-\alpha_i$ for $i\in G$.  We claim that $\varphi(\nu_i)\geq-\alpha_i$ for $i\notin G$ by the fact that the hyperplane $x_i=-\alpha_i$ does not intersect $P_\alpha$.

  Fix $i\notin G$.  Since $\Sigma$ is the normal fan of a polytope it is complete, so we can write $\nu_i=\sum\beta_j\nu_j$ for $\beta_j>0$ and $\nu_j$ the rays of a single cone in $\Sigma$.  By the definition of a support function $\varphi$ is linear within the cone spanned by the $\nu_j$, so that $\varphi(\nu_i)=\sum\beta_j\alpha_j$.
\end{proof}

By \cite[Proposition 14.4.3]{CLS} the projection $\Gamma(Q,V)$ of $\tilde\Gamma(\Sigma,F)\subseteq\QQ^n$ to $\Cl(S)\otimes_\ZZ\QQ$ is a strongly convex rational polyhedral cone.  \lauren{get polytope from support function and describe when it is nonempty?}

\begin{rem}
  We have largely chosen to use polytopes instead of fans because we find the pictures of facets varying over the secondary fan to be more intuitive, and because we want to restrict the use of generalized fans and support functions to the discussion above.  The existence of~$\varphi$ on the fan $\Sigma$ requires the class $\deg\alpha$ to be nef on the toric variety of the generalized fan $\Sigma$, and the vector space structure on support functions clarifies the cone structure of $\Gamma(\Sigma,V)$.
\end{rem}

\begin{prop}[\cite{OdaPark91}*{Corollary 3.6},\cite{CLS}*{Theorem 14.4.7}]\label{prop:fan-structure}
  The collection of cones $\Gamma(Q,V)$ forms an $n$-dimensional rational polyhedral fan in $\Cl(S)\otimes_\ZZ\QQ$, known as the \emph{secondary fan} of the ring $S$ graded via $\deg\colon\ZZ^n\to\Cl(S)$.  We call maximal cones of this fan \emph{chambers}.
\end{prop}

\begin{example}
  \lauren{more complicated polytope than Hirzebruch}
\end{example}

We will see in Theorem~\ref{thm:GIT-polytope} that the toric variety $X_d$ discussed in Section~\ref{sec:variation-of-GIT} is determined by the polytope $P_\alpha$ with $\deg\alpha=d$.  However this polytope may have nonintegral vertices, requiring a slight generalization of the standard construction.

Given a full-dimensional rational polytope $P$ in $M\otimes_\ZZ\QQ$ and a vertex $v$ of $P$, take the cone of the set $P\cap(M\otimes_\ZZ\QQ)-v$ in $M\otimes_\ZZ\QQ$.  Over all vertices, the duals of these form the maximal cones of a fan in $N\otimes_\ZZ\QQ$ by \cite[Proposition 14.2.10]{CLS}, which also addresses the situation when $P$ is not full dimensional.  This process reduces to the standard construction of the normal fan of a polytope when its vertices are integral.  The toric variety of $P$ is then defined by the resulting fan.

\begin{thm}[\cite{CLS}*{Theorem 14.2.13(b)}]\label{thm:GIT-polytope}
  Suppose that $\alpha\in\QQ^n$ and $d=\deg\alpha$ is in the interior of a chamber of the secondary fan of $S$.  The toric variety of the polytope $P_\alpha$ is isomorphic to the quotient $X_d$ of $\Spec S$ by $G$ as given in Corollary~\ref{cor:quotient-Proj}.
\end{thm}

A version of Theorem~\ref{thm:GIT-polytope} is true for all $d\in\Cl(S)$ but may involve a lower dimensional polytope.  As a consequence, the toric variety $X_d$ is constant within the interior of each cone of the secondary fan.  Varieties from distinct chambers will have distinct normal fans, though they may be isomorphic via a nontrivial map of lattices.  \lauren{reference stacky discussion earlier to briefly discuss walls?}

\begin{cor}
  Suppose that $d,d'\in\Cl(S)$ are contained in the interior of the same chamber of the secondary fan of $S$.  Then $X_d\cong X_d'$ via the identity map on the lattice $N$.
\end{cor}

\begin{proof}
  Choose $\Sigma$ a fan and $F\subseteq\{1,\ldots,n\}$ so that $d,d'\in \Gamma(\Sigma,F)$, and choose $\alpha,\alpha'\in\QQ^n$ so that $\deg\alpha=d$ and $\deg\alpha'=d'$.  By definition of $\Gamma(\Sigma,F)$ we have $\alpha,\alpha'\in\tilde\Gamma(\Sigma,F)$.  By Lemma~\ref{lem:GKZ-def} and Proposition~\ref{prop:fan-structure} the normal fans of $P_\alpha$ and $P_{\alpha'}$ must both be $\Sigma$.  By Theorem~\ref{thm:GIT-polytope} the varieties $X_d$ and $X_{d'}$ are both defined by this fan so they are isomorphic via the identity map.
\end{proof}

\lauren{describe nef cones here, or somewhere else?}

\subsection{Irrelevant ideals}\label{sec:irrelevant-ideals}

%In other words, we want to determine the various toric varieties (or toric stacks) that can arise from a given multigraded polynomial ring.   This requires some additional notation. We first define a correspondence between convex cones in $\Cl(S)\otimes \QQ$ and squarefree monomial ideals in $S$.

\begin{defn}\label{defn:idealConeCorrespondence}
  Fix a monomial $\mathbf{x}^{\mathbf{a}} \ce x_1^{a_1}\cdots x_n^{a_n}$ and a point $d\in \Cl(S)\otimes \QQ$.  We say \defi{$\mathbf{x}^{\mathbf{a}}$~spans~$d$} \lauren{what is this font?}
  %\[d \in \QQ_{>0} \cdot \{ \{\deg_{\QQ}(x_i) \ | \ a_i \ne 0\} \}
  %\]the positive, rational cone spanned by $\{\deg_{\QQ}(x_i) \ | \ a_i %\ne 0\}$ contains $d$, i.e.
  if there exist $q_i>0$ such that
  $
  d = \sum_{i} q_i\deg_{\QQ}\mathbf a).
  $
  \lauren{$\mathbb{Q}$ notation} For a convex cone $\Gamma \subseteq \Cl(S)\otimes \QQ$, let
  \[
  \text{ideal}(\Gamma) \ce \langle \mathbf{x}^{\mathbf{a}}\  | \ \mathbf{x}^{\mathbf{a}} \text{ spans } d \text{ for all } d\in \Gamma\}.
  \]
  Conversely, given a monomial ideal $B$, let
  \[
  \text{cone}(B) \ce \{ d\  | \ \mathbf{x}^{\mathbf{a}} \text{ spans } d\text{ for all } \mathbf{x}^{\mathbf{a}} \in B\}.
  \]
\end{defn}
The monomial $\mathbf{x}^{\mathbf{a}}$ spans $d$ if and only if the squarefree monomial containing the same variables spans $d$, so $\text{ideal}(\Gamma)$ is a squarefree monomial ideal in $S$.
%and $\text{cone}(B)$ is an open convex cone in $\Cl(S)\otimes \QQ$.
It is elementary to check that
\[
\text{ideal}(\text{cone}(\text{ideal}(\Gamma))) = \text{ideal}(\Gamma) \qquad \text{ and } \qquad \text{cone}(\text{ideal}(\text{cone}(B))) = \text{cone}(B).
\]

\lauren{do we want to define this notation, or do we just want a theorem that this is how you get the irrelevant ideal of $X_d$ from the chamber of $d$?}

Since there are only a finite number of squarefree monomial ideals in $S$, it follows that there is a finite list of squarefree monomial ideals $B_1, \dots, B_s$ such that $\text{cone}(B_i)$ is both full-dimensional and satisfies the relation $B_i = \text{ideal}\left(\text{cone}(B_i)\right) $. These are the chambers of the secondary fan.

Each ideal $B_i$ in Definition~\ref{defn:chambersIrrelevant} determines a corresponding fan $\Sigma_i$.  There are several alternate ways to recover a toric variety from a chamber $\Gamma_i$, and the main theorem is that they all yield $X_i$: \lauren{this theorem has largely been absorbed by the previous exposition}

\begin{thm}
  \label{thm:mainsecondary}
  Fix a chamber $\Gamma_i\subseteq \Eff(X)$ for some $1\leq i \leq s$. Let $B_i$ the corresponding square-free maximal ideal, $\Sigma_i$ the associated fan, and $X_i$ as in Definition~\ref{defn:Xi}. Write $G \ce \Hom(\Cl(X), \kk^*)$.   We have the following:
  \begin{enumerate}
    \item  {\bf Simplicial:}  $\Sigma_i$ is a simplicial fan whose rays are a subset of the rays of $\Sigma$ and such that~$|\Sigma_i| = |\Sigma|$. In particular, $X_i$ is a projective, simplicial toric variety.
    \item   {\bf Quotient:}  $\Spec(S) - V(B_i)\to X_i$ is a geometric quotient as in~\cite[Chapter 5]{CLS}.
    %	\item  {\bf Toric stack:}   $[\Spec(S) - V(B_i) / G]$ is a smooth toric DM stack with coarse moduli space equal to $X_i$.
  \end{enumerate}

  Choose any point $a=(a_1, \dots, a_n) \in \ZZ^n$ such that $\deg_{\QQ}(a)$ lies in the interior of $\Gamma_i$.
  We also have the following:
  \begin{enumerate}\setcounter{enumi}{2}
    \item  {\bf Proj:}  Let $S_a$ be the $\ZZ$-graded ring
    $
    S_{a} = \bigoplus_{e\geq 0} S_{ea}.
    $
    We have $\Proj(S_a)=X_i$.
    %Moreover, if $u_\tau$ is the primitive point on the ray $\tau$ then the divisor corresponding $eu_{\tau}$ equals $S_\tau(e)|_{X_i}$.
    \item   {\bf Normal fan:}  Let $P_a\subseteq M$ be the polytope
    $
    P_{{a}} \ce \bigcap_{i=1}^n \{ m \in M \text{ $|$ } \alpha_i(m) \geq -a_i\},
    $
    where $\alpha_i$ is given by composing the canonical map $M \into \Z^n$ with the projection onto the $i^{\th}$ coordinate. The normal fan of $P_a$ is $\Sigma_i$.
    %	\item
  \end{enumerate}
  Moreover, $\widetilde{S_{a}(1)}$ is equal to the rank one torsion free sheaf associated to the polytope $P_a$.
\end{thm}
\begin{proof}
  %Part (3) follows from \cite{BorisovChenSmith2004}*{\S 3}
  All of these results can be extracted from \cite[Chapters 14-15]{CLS}, but those are pretty technical paragraphs so it is not so easy to find an overarching statement like this.  Statement (1) essentially follows from~\cite[Proposition 14.4.9]{CLS}.  Statement (2) follows from ~\cite[Proposition 14.4.14]{CLS} combined with the fact from \cite[Theorem 5.1.11]{CLS} that for a simplicial toric variety, the quotient is a geometric quotient.
  %\daniel{Mostly just cite the places in CLS?}
\end{proof}

\section{Nef and moving cones}

\lauren{turn this into a subsection about what happens when you lose a ray}

The previous example \lauren{now somewhere else} illustrates that the varieties $X_1, \dots, X_r$ arising in the secondary fan come in two basic flavors:  those whose Cox ring equals the original $S$ (these lie in the ``moving cone'') and those whose Cox rings involve fewer variables.  The former toric varieties are more obviously related to the Cox ring $S$, and the following lemma provides equivalent characterizations of them:
\begin{lemma}\label{lem:MovingConeEquivalence}
  The following are equivalent:
  \begin{enumerate}
    \item The Cox ring of $X_i$ equals $S$;
    \item $\Cl(X_i)=\Cl(S)$;
    \item  The rays of $\Sigma_i$ are precisely $\rho_1, \dots, \rho_n$;
    \item  $B_i$ does not belong to any principal ideal $\langle x_j\rangle$.
  \end{enumerate}
\end{lemma}
\begin{proof}[Sketch of proof]
  For each $X_i$, the rays of $\Sigma_i$ are a subset of $\rho_1, \dots, \rho_n$~\cite[ Chapter 14.4]{CLS}.  Since the Cox ring of $X_i$ is a polynomial ring whose variables are in bijection the rays of $\Sigma_i$, this yields the equivalence of (1) and (3).  If any of the rays $\rho_j$ does not arise in $\Sigma_i$, then the vanishing of the corresponding variable $x_j$ defines the empty set on $X_i$ and thus $x_j$ form a minimal component of $B_i$.  This yields the equivalence of (3) and (4).  The equivalence of (2) and (3) comes from the short exact sequence \eqref{eqn:SESCl}.

\end{proof}
\begin{remark}\label{rmk:abuseNotation}
  By a mild abuse of notation, we will refer to $B_i\subseteq S$ as \defi{the irrelevant ideal of $X_i$}.  Why is this an abuse of notation?  When the Cox ring of $X_i$ equals $S$, i.e. when the conditions of Lemma~\ref{lem:MovingConeEquivalence} are satisfied, this is not an abuse of notation; in that case, $B_i$ is precisely the irrelevant ideal of $X_i$, in the standard definition.  But as we have seen, it can happen that the Cox ring of $X_i$ does not equal $S$.  This happens precisely when the fan $\Sigma_i$ does not involve all of the original rays.  In this case, at least one of the variables $x_j$ from the original ring $S$ will not appear in the Cox ring of $X_i$.

  Considering our running Example~\ref{ex:hirzSecondary} is helpful: one of the varieties is $\PP(1,1,3)$ whose fan does {\em not} involve the ray $\rho_1 = (0,1)$.  Thus, the Cox ring of $\PP(1,1,3)$ would be a polynomial ring involving only $3$ variables, and a $\Cl(\PP(1,1,3)) = \ZZ$-grading, as opposed to $S$ itself which has $4$ variables and a $\ZZ^2$-grading.

  However, we can recover $\PP(1,1,3)$ from $S$ with the $\ZZ^2$-grading by including the variable $x_1$ but then making it into a component of the irrelevant ideal.  Thus, we set $B_2 = \langle x_1\rangle \cap \langle x_0,x_2,x_3\rangle \subseteq S$.  Theorem~\ref{thm:mainsecondary} tells us that with this definition, we still recover $\PP(1,1,3)$ as a quotient of $\Spec(S) - V(B_2)$.

  It would be more accurate to think of $B_i$ as the irrelevant associated to the chamber $\Gamma_i$, as opposed to the irrelevant ideal associated to $X_i$.  This viewpoint is developed in greater detail in ~\cite[\S7]{BEF}.
\end{remark}





When the conditions of Lemma~\ref{lem:MovingConeEquivalence} are satisfied, the ample cone equals $\Gamma_i$.  When these conditions are not satisfied, one needs to be more careful, as $\Gamma_i\subseteq \Cl(S)\otimes \QQ \ne \Cl(X_i)\otimes \QQ$.
(Note:  the more common notation for this sheaf is $\widetilde{M}$, however when considering a single module with respect to different toric varieties, it is useful to have a notation that also specifies the toric variety $X_i$.)
\medskip
We saw in an earlier lecture that if $X_i$ satisfies the conditions of Lemma~\ref{lem:MovingConeEquivalence}, a (finitely generated) $\Cl(S)$-graded $S$-module $M$ induces a (coherent) sheaf $\widetilde{M}$ on $X_i$.

\begin{notation}
  To emphasize the dependence of $\widetilde{M}$ on $X_i$, we will from now on write $\widetilde{M}$ as $M|_{X_i}$.
\end{notation}A minor modification of the associated sheaf construction works for the other $X_i$'s as well. We therefore have:
\begin{prop}
  Let $X_i$ be any of the simplicial toric varieties from Definition~\ref{defn:Xi} and let $\cE$ be a quasi-coherent sheaf on $X_i$.
  \begin{enumerate}
    \item There exists a graded $S$-module $M$ such that $M|_{X_i}\cong \cE$.
    \item  If $\cE$ is coherent then $M$ can be chosen to be a finitely generated $S$-module
  \end{enumerate}
\end{prop}

%We will in the next lecture see  this correspondence is simpler to describe if one passes to the toric stack associated to~$X_i$ (in fact, this is the {\em main} reason to talk about stacks, in our opinion).


%, and thus the following construction is not necessary for the main results about Cox categories.  However, for those familiar with the relationship between modules on a Cox rings and sheaves on a toric variety, it may provide a helpful perspective.












%\begin{thm}
%The chamber s are in bijection with any of the following:
%\begin{enumerate}
%	\item Simplicial toric varieties  with a subset of the given rays
%	\item GIT quotients that arise in a a simplicial toric variety
%	\item  The coarse moduli space of the quotient stack $[\Spec(S) - V(B_i) / G]$ equals $X_i$.
%	\item  Choose any point $a\in \Cl(S)$ where $\deg_{\QQ}(a)$ lies in the interior of $\Gamma_i$.  Let $P_a\subseteq M$ be associated polytope and let $\Sigma$ be the normal fan of $P_a$.  The toric variety associated to $\Sigma$ is $X_i$.
%%	\item
%\end{enumerate}
%\end{thm}


%\begin{remark}
%     We will confirm below that each pair $(S,B_i)$ determines a simplicial projective variety $X_i$.  The rough statement is that $X_i$ the quotient $\Spec(S) - V(B_i) / G$ (with the action of $G$ induced by the grading group), but this is a ``rough'' statement because of various subtleties involving quotients of projective varieties.  So there is a sense in which the multigraded ring $S$ naturally corresponds to the set of toric varieties $X_1, \dots, X_r$.
%
%    This connection is even sharper from a homological perspective.  The pair $(S,B_i)$ determines a module category as follows:  we write $\mod(S)$ for the category of $\Cl(S)$-graded $S$-modules and we write $\mod_{B_i}(S)$ for the subcategory  modulo those modules that are annihilated by a power of $B_i$.  To the pair $(S,B_i)$ we can attach the quotient category $\mod(S)/\mod_{B_i}(S)$.  This equals--essentially by defintion--the category of sheaves on the quotient stack $[\Spec(S) - V(B_i)/G]$ which we denote as $\mathcal X_i$.  We will see later that $\mathcal X_i$ is closely related to the aforementioned toric variety $X_i$.
%\end{remark}

\ifdefined\whole
\else
\bibliographystyle{plain}
\bibliography{Bibliography}
\end{document}
\fi
