\ifdefined\whole
\else
\documentclass{amsart}
\input{preamble}
\begin{document}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 18 (Matthias Zach): Tate resolutions over projective space}\label{lec:18-tate-resolutions-PPn}

Let $S = \k[x_0, \dots, x_n]$, $\Z$-graded with $\deg(x_i) = 1$, and let $E = \bigwedge_\k(e_0, \dots, e_n)$ be the exterior algebra with $\deg(e_i) = -1$. Let $E^*$ denote the $\k$-dual of $E$. We saw on Monday that there is an equivalence of categories
$
R \co D^b(S) \xra{\simeq} D^b(E)
$
that sends a finitely generated module $M$ (thought of as a complex concentrated in homological degree 0) to
\begin{equation}
\label{eqn:RMformula}
R(M) = \left[\cdots \xla{\del_R} E^*(i) \otimes_\k M_{-i} \xla{\del_R} E^*(i + 1) \otimes_\k M_{-i - 1} \xla{\del_R} \cdots \right],
\end{equation}
where $E^*(i) \otimes_\k M_{-i}$ is in homological degree $-i$. Moreover, we saw that we get an induced equivalence
\begin{equation}
\label{eqn:geobgg}
\overline{R} \co D^b(\PP^n) \xra{\simeq} D^{\on{sing}}(E) \ce D^b(E) / \Perf(E),
\end{equation}
where $D^{\on{sing}}(E)$ denotes the singularity category of $E$, and $\Perf(E)$ is the category of perfect complexes in $E$. We recall that the objects in $D^{\on{sing}}(E)$ are the same as those in $D^b(E)$, but the morphisms are obtained by inverting all morphisms in $D^b(E)$ whose mapping cone lies in $\Perf(E)$. The equivalence~\eqref{eqn:geobgg} gives a ``geometric" version of the BGG correspondence, though an unsatisfying one: the passage from $D^b(S)$ to $D^b(\PP^n)$ translates to the passage from $D^b(E)$ to $D^{\on{sing}}(E)$, which is only visible at the level of morphisms. Since the morphisms in $D^{\on{sing}}(E)$ are essentially unknowable, this renders the projective geometry in $D^{\on{sing}}(E)$ effectively invisible. This problem is solved by Eisenbud-Fl\o ystad-Schreyer's theory of Tate resolutions~\cite{EFS}, and the goal of this lecture is to explain this theory.

Conceptually, we need a way to get our hands on the morphisms in $D^{\on{sing}}(E)$. There is a classical method for making the morphisms in a derived category explicit, namely by replacing it with an appropriate homotopy category. For instance, $D^b(E)$ is equivalent to the homotopy category $K^-(E)$ of complexes of finitely generated graded free $E$-modules whose terms vanish in large homological degrees. In the case of an exterior algebra, this equivalence may be given by taking the $\k$-dual of a minimal free resolution\footnote{It makes sense to take a (minimal) free resolution of any complex of finitely generated $E$-modules with bounded homology~\cite{Rob98}*{Proposition 4.4.1}.}. There is a similar result for the singularity category, due to Buchweitz~\cite{buc21}*{Theorem 4.4.1}, and this is the added ingredient we need. Specifically: there is an equivalence
\begin{equation}
\label{eqn:buchweitz}
B \co D^{\on{sing}}(E) \xra{\simeq} K(E),
\end{equation}
where $K(E)$ is the homotopy category of (possibly unbounded on both sides) exact complexes of finitely generated graded free $E$-modules. This equivalence sends an object $C$ in $D^{\on{sing}}(E)$ to the mapping cone of the canonical quasi-isomorphism $G \to F$, where $G$ is the minimal free resolution of the $\k$-dual of $N$, and $F$ is the $\k$-dual of the minimal free resolution of~$N$. We arrive at the following key commutative diagram:
\begin{equation}
\label{eqn:tatediagram}
\xymatrix{
D^b(S) \ar[d] \ar[r]_-{\simeq}^-{R} & D^b(E) \ar[d] \ar[r]_-{\simeq} & K^-(E) \ar[d] \\
D^b(\PP^n) \ar[r]^-{\overline{R}}_-{\simeq} & D^{\on{sing}}(E) \ar[r]_-{\simeq}^B & K(E). \\
}
\end{equation}
The only functor here we have not yet described is the rightmost vertical one, which sends an object~$F$ to $\cone(G \xra{\simeq} F)$, where $G$ is the minimal free resolution of~$F$.

With all this in mind, let us now give an alternative formulation of the BGG correspondence for~$\PP^n$. Essentially, it is given by composing the functors in the bottom row of Diagram~\eqref{eqn:tatediagram}. To obtain an explicit and geometrically meaningful formula for this composition, we proceed as follows. Let $\F$ be a coherent sheaf on $\PP^n$, and let $M$ be a finitely generated graded $S$-module such that $\widetilde{M} = \F$. Fix $s > \reg(M)$, the Castelnuovo-Mumford regularity of $M$. Let $G$ be the minimal free resolution of $R(M_{\ge s})$, and let $T(\F)$ be the mapping cone of the quasi-isomorphism $G \xra{\simeq} R(M_{\ge s})$. Since $T(\F)$ is the mapping cone of a quasi-isomorphism, it is exact. Since any two finitely generated graded modules representing $\F$ are isomorphic in large degrees, $T(\F)$ is well-defined up to the choices of $M$ and $s$, up to chain isomorphism. 


\begin{defn}[\cite{EFS}*{Section 4}]
The complex $T(\F)$ is called the \emph{Tate resolution of $\F$.} 
\end{defn}

\begin{example}
\label{ex:tate}
Say $S = \k[x_0, x_1]$. Take $M = S / (x_0)$, and $\F = \widetilde{M}$, the structure sheaf of a point on $\PP^1$. The regularity of $M$ is 0, so there is no need to truncate. We have 
$$
R(M) = \left[ \cdots \xla{e_1} E^*(-2) \xla{e_1} E^*(-1) \xla{e_1} E^* \from 0 \right].
$$
This complex is exact except in homological degree 0. So to get the Tate resolution, we just need to resolve its $0^{\th}$ homology, which gives:
$$
T(\F) = \left[
\cdots  \xla{e_1} E^*(-1) \xla{e_1} E^* \xla{e_1} E^*(1) \xla{e_1} \cdots
\right].
$$
\end{example}


The next result demonstrates that the Tate resolution functor is a model for the BGG correspondence~$D^b(\PP^n) \xra{\simeq} K(E)$ applied to sheaves.


\begin{prop}
\label{prop:tateBR}
For any coherent sheaf $\F$ on $\PP^n$, we have $T(\F) = (B \circ \overline{R})(\F)$. %In particular, $T(\F)$ is well-defined (up to homotopy equivalence) up to the choice of module $M$ such that $\widetilde{M} = \F$ and the choice of $s > r$. 
\end{prop}


\begin{proof}
This follows from the commutativity of Diagram~\eqref{eqn:tatediagram}: the formula for $T$ lifts $\F$ to $D^b(S)$ and then applies the top two horizontal and right most vertical functors in the diagram. 
\end{proof}

In Example~\ref{ex:tate}, we only needed to resolve a single module, not a complex with nonzero homology in multiple positions. An advantage to using the truncation $M_{\ge s}$ in the definition of the Tate resolution is that this always happens: $R(M_{\ge s})$ has nonzero homology only in degree $-s$, so 
so $G$ is just the minimal free resolution of $H^{-s}(R(M_{\ge s}))$. Let us give a quick sketch of a proof of this fact, as we will need it later. We will use the following technical lemma:

\begin{lemma}[\cite{EFS}*{Proposition 2.3(a)}]
\label{lem:tor}
For any graded $S$-module $M$, we have $H_i(R(M)) \cong \Tor^S_{i+j}(M, \k)_j$.
\end{lemma}


\begin{proof}[Sketch of proof]
The idea is that, forgetting gradings, $R(M)$ is isomorphic to $M \otimes_S K$, where $K$ is the Koszul complex on the variables in $S$. The proof thus boils down to keeping careful track of how this isomorphism interacts with the homological and internal gradings; we omit the details. 
\end{proof}

\begin{prop}
If $M$ is a finitely generated graded $S$-module with regularity $r$, then $R(M_{\ge r})$ has nonzero homology only in degree $-r$. 
\end{prop}

\begin{proof}
Since $M_{\ge r}$ has a linear free resolution~\cite{EG}, this follows immediately from Lemma~\ref{lem:tor}.
\end{proof}

 The following is one of the main theorems of \cite{EFS}: 






\begin{thm}
\label{thm:tate1}
Let $\F$ be a coherent sheaf on $\PP^n$. Its Tate resolution $T(\F)$ is minimal, and for all $i, j \in \Z$, there is an isomorphism $T(\F)_i \cong \bigoplus_{j \in \Z} E^*(i + j) \otimes_\k H^j(\PP^n, \F(-i - j))$.
\end{thm}

Theorem~\ref{thm:tate1} tells us how to actually see projective geometry via BGG: the terms of the Tate resolution of~$\F$ encode the sheaf cohomology of all the twists of $\F$. That is, the Buchweitz equivalence~\eqref{eqn:buchweitz} pulls the geometry out of the morphisms in the singularity category and expresses  it via the objects of $K(E)$.

\begin{example}
Let us return to Example~\ref{ex:tate}. Since $\F$ is the structure sheaf of a point, we have
$$
H^0(\PP^1, \F(i)) = 1 \quad \text{for all $i$,} \quad H^j(\PP^1, \F(i)) = 0 \quad \text{for all $i, j$.}
$$
One sees this immediately from the terms of $T(\F)$ using Theorem~\ref{thm:tate1}. 
\end{example}

\begin{remark}
\label{rem:truncation}
Let $\F$ be a sheaf on $\PP^n$ and $M$ an $S$-module such that $\widetilde{M} = \F$. If we defined the Tate resolution of $\F$ without truncating past the regularity of $M$, Theorem~\ref{thm:tate1} would become false. For instance, take~$\F = 0$. Of course, we have $\widetilde{\k} = \F$. If we applied the formula for the Tate resolution without truncating~$\k$, we would get the complex $E \xla{1} E$. This is not a minimal complex, and the ranks of its terms clearly do not correspond to the ranks of the cohomologies of the twists of $\F$, which are all zero. 
\end{remark}

\begin{proof}[Proof of Theorem~\ref{thm:tate1}]
We will sketch a proof of the formula for the terms of $T(\F)$ in greater generality in the next lecture. Concerning minimality: let $M$ be a finitely generated graded $S$-module such that $\widetilde{M} = \F$, and let $r$ be the regularity of $M$. Recall that $R(M_{\ge r})$ has cohomology concentrated in degree $-r$ \cite{EFS}*{Corollary 2.4}. Let $\m_E$ be the homogeneous maximal ideal of $E$. The complex $G$ is the minimal free resolution of the kernel of the first nonzero differential in the minimal complex $R(M_{\ge s})$. So we just need to check that the quasi-isomorphism $G \xra{\simeq} R(M_{\ge s})$ takes values in $\m_E \cdot R(M_{\ge s})_{-s} = \m_E(-s) \otimes_\k M_s$. Equivalently, we must show that the kernel of the first nonzero differential in $R(M_{\ge s})$ is contained in $\m_E(-s) \otimes_\k M_s$. This is holds since $R(M_{\ge r})$ is exact in homological degrees less than $-r$. 
\end{proof}

\begin{remark}
The differentials in Tate resolutions, while readily computable in Macaulay2, remain somewhat mysterious. That is, it is not known how to describe them geometrically in general, though progress on this has been made in some special cases, e.g.~\cite{cox07,cm}. 
\end{remark}

Tate resolutions have had a host of applications; let us highlight two of them. The first is an effective method for computing a Beilinson monad of a sheaf on $\PP^n$, by which we mean a complex of the form
\begin{equation}
\label{eqn:monad}
\cdots 
\from 
\bigoplus_{i = 0}^n H^j(\F(j-i+1)) \otimes_\kk \Omega_{\PP^n}^{i-j-1}(i-j - 1) 
\from
\bigoplus_{i = 0}^n H^i(\F(j-i)) \otimes_\kk \Omega_{\PP^n}^{i-j}(i-j)\from \cdots 
\end{equation}
that is quasi-isomorphic to the sheaf $\F$. This complex is typically obtained via a Fourier-Mukai transform with kernel given by the Beilinson resolution of the diagonal, but, from this point of view, it is not easy to compute the differentials in~\eqref{eqn:monad}, even with the aid of Macaulay2. The insight of \cite{EFS}*{Section 6} is that one can first compute the Tate resolution $T(\F)$ (which is easy and efficient to do in Macaulay2) and then apply a simple, computable functor to $T(\F)$ to obtain the monad~\eqref{eqn:monad}. These ideas were also applied in Eisenbud-Schreyer's subsequent work on Chow forms~\cite{ES-JAMS}. 

The second application is an algorithm for computing sheaf cohomology over $\PP^n$ by applying the formula in Theorem~\ref{thm:tate1}. This is, in some cases, the fastest known way to compute cohomology over $\PP^n$~\cite{decker-eisenbud}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 19 (Sasha Zotine): Tate resolutions over toric varieties}\label{lec:19-tate-resolutions-toric}

Eisenbud-Fl\o ystad-Schreyer's theory of Tate resolutions~\cite{EFS} was extended to products of projective spaces in \cite{EES} and later generalized further to toric varieties in \cite{BETate}. The goal of this lecture is to give an overview of this latter paper.  

Let $\X$ be the toric stack associated to a simplicial projective toric variety $X$. As discussed earlier, if $X$ is smooth, then $\X = X$. Let $S = \k[x_0, \dots, x_n]$ be the Cox ring of $X$, equipped with its $\Cl(X)$-grading. To ease notation, we write $A \ce \Cl(X)$ in these notes. To generalize Tate resolutions to sheaves on $\X$, the first thing we need to do is extend the BGG correspondence to $A$-graded polynomial rings. This already introduces a complication: in the standard graded case, the internal grading on a module $M$ over the polynomial ring induces the homological grading on the complex $R(M)$. This cannot possibly work when the $A$-grading is nonstandard. The solution to this problem is to widen our perspective from complexes of exterior modules to \emph{differential modules}. Before explaining what we mean, we fix some notation. Let $E = \bigwedge_\k(e_0, \dots, e_n)$, equipped with the $A \times \Z$-grading such that $\deg(e_i) = (-\deg(x_i); -1)$. 

\begin{defn}
A \emph{differential $E$-module} is an $A \oplus \Z$-graded right $E$-module $D$ equipped with an $E$-linear endomorphism $\del_D$ of degree $(0;-1)$ such that $\del_D^2 = 0$. A \emph{morphism} of these objects is the obvious thing: an $E$-linear degree $(0;0)$ map that commutes with differentials. 
\end{defn}

\begin{remark}
We can think of $E$ as a differential graded (dg) algebra with homological grading given by $\deg(e_i) = -1$, internal grading given by $\deg(e_i) = -\deg(x_i)$, and trivial differential. The category of dg-modules over this dg-algebra is equivalent to $\DM(E)$. An advantage to repackaging this data as a differential $E$-module is that it makes computation in Macaulay2 a bit simpler. 
\end{remark}

Let $\on{mod}(S)$ be the category of $A$-graded $S$-modules, and let $\DM(E)$ be the category of differential $E$-modules. The $A$-graded BGG functor
$$
R \co \on{mod}(S) \to \DM(E)
$$
sends $M \in \on{mod}(S)$ to $\bigoplus_{a \in A} E^*(-a;0) \otimes_\k M_a$, with differential given by multiplication on the left by $\sum_{i = 0}^n e_i \otimes x_i$. The functor $R$ extends naturally to complexes of $A$-graded $S$-modules, and it has a left adjoint, just as in the classical setting. In fact, the functor $R$ induces an equivalence $D^b(S) \xra{\simeq} D^b_{\DM}(E)$, where the target is the bounded derived category of differential $E$-modules, i.e. the category of differential $E$-modules with finetely generated homology with quasi-isomorphisms inverted. The proof of this is somewhat delicate; we omit the details. 

\begin{remark}
\label{rem:stdm}
When $S$ is standard graded, there is an equivalence between $\DM(E)$ and the category of complexes of $\Z$-graded $E$-modules, where $\deg(e_i) = -1$. The BGG functor we defined above coincides with the classical one via this equivalence. 
\end{remark}

\begin{example}[\cite{BE25comp}*{Example 3.3}]
\label{ex:ellipticCurve}
Let us consider the case of the weighted projective stack $\PP(1,1,2)$, so that $\Cl(X) = \Z$, and $S = k[x_0, x_1, x_2]$ with $\deg(x_0) = 1 = \deg(x_1)$ and $\deg(x_2) = 2$. Let $M= S/(x_0^4+x_1^4+x_2^2)$ be the coordinate ring of a genus $1$ curve in $\PP(1,1,2)$.  The differential module $R(M)$ is an infinitely generated free $E$-module whose generators are in bijection with a $\kk$-basis for $M$.  In this example, we have
$\dim_\k M_0 = 1$, and $\dim_\k M_i = 2i$ for $i \ge 1$.
Thus, $R(M)$ has the form:
\vskip\baselineskip
\footnotesize
\[
R(M) = \xymatrix{
E^* \ar[r]^-{}\ar@/_2pc/[rr]_-{}& E^*(-1;0)^{\oplus 2} \ar[r]^-{}\ar@/_-2pc/[rr]^-{}&E^*(-2;0)^{\oplus 4} \ar[r]^-{}\ar@/_2pc/[rr]_-{} &E^*(-3;0)^{\oplus 6}\ar[r]^-{} & \cdots
}
\]
\normalsize
The above graphic is an attempt to represent a differential module, not a complex.  To be more precise, we choose monomial bases for each $M_i$, e.g. $\{1\}, \{x_0,x_1\}$ and $\{x_0^2,x_0x_1,x_1^2, x_2\}$ for $M_0, M_1$ and $M_2$, respectively.  The differential $\partial$ sends the generator $1 \in E^*$ to $e_0\otimes x_0 + e_1\otimes x_1 + e_2\otimes x_2$.  This element lies in the direct sum $E^*(-1;0)^{\oplus 2} \oplus E^*(-2; 0)^{\oplus 4}$.  This is indicated in the above graphic by the arrows emanating from $E^*$.  %For any $r \ge 0$, $R(M_{\ge r})$ may be depicted by removing all summands of the form $E^*(-d ; 0)$ for $d < r$ from the picture above.
\end{example}

Let us now turn to Tate resolutions. We want an equivalence between $D^b(\X)$ and some homotopy category of differential $E$-modules. Moreover, we want a formula for this equivalence that is geometrically meaningful, which is what the theory of Tate resolutions over $\PP^n$ provides (see Theorem~\ref{thm:tate1}).  

Naively generalizing the formula for Tate resolutions from the previous lecture doesn't work: let us explain why. Recall that one defines the Tate resolution of a sheaf $\F$ on $\PP^n$ by choosing a graded module $M$ such that $\widetilde{M} = \F$, taking the minimal free resolution $G$ of $R(M_{\ge s})$ where $s > \reg(M)$, and setting $T(\F) = \cone(G \xra{\simeq} R(M_{\ge s}))$. This recipe can't possibly work in the toric case, because the entire construction only depends on the Cox ring $S$: the irrelevant ideal never enters in. It therefore can't fully capture $D^b(\X)$.

We therefore proceed as follows. The maximal cones of $\Sigma$ determine a $G$-invariant affine open cover of $Z$~\cite{BCS05}*{\S 4}. Given a complex $\F$ of quasi-coherent $\OO_\X$-modules, we let $\cC(\F)$ denote the \v{C}ech complex of $\F$ with respect to this open cover, and we let $\cC_*(\F)$ be the complex $\bigoplus_{a \in \Cl(X)} \cC(\F(a))$ of $\Cl(X)$-graded $S$-modules. Let $\coh(\X)$ (resp. $\Com(S)$) denote the category of coherent sheaves on $\X$ (resp. complexes of $A$-graded $S$-modules), and let $\RR\Gamma_* \co \coh(\X) \to \Com(S)$ denote the functor given by $\F \mapsto \cC_*(\F)$. 

\begin{example}
\label{ex:cech}
Let $X$ be the Hirzebruch surface of type $r$. In this case, the canonical affine open cover of $Z$ is given by 
the open sets $\Spec(S) \setminus V(m)$, where $m$ ranges over the set of monomials $M = \{x_0x_1, x_0x_3, x_1x_2, x_2x_3\}$. The complex $\cC_*(\OO_X)$ therefore has the form
$$
S[\frac{1}{x_0 \cdots x_3}] \from \bigoplus_{i = 0}^3 S[\frac{1}{x_0 \cdots \widehat{x_i} \cdots x_3}] \from \bigoplus_{m \in M} S[\frac{1}{m}],
$$
with differential given by the usual signed inclusions. 
\end{example}

We define $\Phi \co \coh(\X) \to \DM(E)$ to be the composition $\RR \circ \RR\Gamma_*$. The idea is that the toric Tate resolution of a sheaf $\F$ on $\X$ is defined to be the minimization of $\Phi(\F)$. More specifically, we have the following, which is implied by \cite{BETate}*{Theorem 3.3}:

\begin{thm}
\label{thm:tate2}
Let $\F \in \coh(\X)$. There exists $T(\F) \in \DM(E)$ with the following properties:
\begin{enumerate}
\item $T(\F)$ is homotopy equivalent to $\Phi(\F)$. 
\item $T(\F)$ is minimal, i.e. its differential takes values in $\m_E \cdot T(\F)$, where $\m_E$ is the homogeneous maximal ideal of $E$
\item For any $a \in \Cl(X)$ and $j \in \Z$, we have $T(\F) \cong \bigoplus_{(a;j) \in A \oplus \Z} H^j(\X, \F(a)) \otimes_\k E^*(-a;j)$.
%\item Let $M$ be a $\Cl(X)$-graded $S$-module such that $\widetilde{M} = \F$ and~$H^0_B(M) = 0$. The canonical injection $M \into \bigoplus_{a \in \Cl(X)} H^0(\X, \F(a))$ induces an injection of differential $E$-modules $R(M) \into T(\F)$. 
\end{enumerate}
Moreover, $T(\F)$ is unique up to isomorphism of differential $E$-modules. 
\end{thm}

\begin{proof}
We can think of $\Phi(\F)$ as a 1-periodic complex
$\left[\cdots \from \Phi(\F)(0;-1) \xla{\del_{\Phi(\F)}} \Phi(\F) \from \cdots \right]$. This complex is the totalization of the following bicomplex:
$$
\xymatrix{
& \vdots \ar[d] && \vdots \ar[d] & \\
\cdots & \ar[l] \bigoplus_{a \in \Cl(X)} \cC(\F(a))^j \otimes_\k E^*(-a; i-1) \ar[d]^-{d^{\text{\v{C}ech}} \otimes 1}&& \ar[ll]_-{\sum_{i = 0}^n x_i \otimes e_i} \ar[d]^-{d^{\text{\v{C}ech}} \otimes 1} \bigoplus_{a \in \Cl(X)} \cC(\F(a))^j \otimes_\k E^*(-a; i) & \ar[l] \cdots \\
\cdots & \ar[l] \bigoplus_{a \in \Cl(X)} \cC(\F(a))^{j+1} \otimes_\k E^*(-a; i-1) \ar[d]  && \ar[ll]_-{-\sum_{i = 0}^n x_i \otimes e_i} \bigoplus_{a \in \Cl(X)} \cC(\F(a))^{j+1} \otimes_\k E^*(-a; i ) \ar[d] & \ar[l] \cdots  \\
 & \vdots && \vdots &
}
$$
(where the $(i, -j)$ position is the top right term). We can use \cite{EFS}*{Lemma 3.5} to minimize the totalization of this bicomplex, and properties (1) - (3) follow immediately from this result. The uniqueness of $T(\F)$ follows from minimality, via the usual Nakayama's Lemma argument. 
\end{proof}

\begin{defn}
\label{defn:torictate}
The \emph{Tate resolution} of $\F \in \coh(\X)$ is the differential $E$-module $T(\F)$ in Theorem~\ref{thm:tate2}. 
\end{defn}

\begin{remark}
If $\F$ is a coherent sheaf on $\X$, and $M$ is a $\Cl(X)$-graded $S$-module such that $\widetilde{M} = \F$ and~$H^0_B(M) = 0$ (where $B$ is the irrelevant ideal of $X$), there is an injection $\RR(M) \into T(\F)$. When~$X = \PP^n$, Remark~\ref{rem:stdm} implies that $T(\F)$ may be considered as a complex of exterior modules, and one can show that it is the minimal free resolution of this embedded copy of $\RR(M)$. This demonstrates that Definition~\ref{defn:torictate} recovers the classical definition over $\PP^n$.

In fact, 
\end{remark}


\ifdefined\whole
\else
\bibliographystyle{plain}
\bibliography{Bibliography}
\end{document}
\fi