%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ifdefined\whole
\else
\documentclass{amsart}
\input{preamble}
\begin{document}
\fi

\section{Lecture 14 (Milena Hering): Proof of revised King's conjecture, I: Outline}\label{lec:14-proof-outline}
The Revised King's Conjecture claims that the line bundles $\cO_{\Cox}(-d)$ for $-d$ in the Bondal-Thomsen collection form a full strong exceptional collection.  Why would this be true and how could we prove this?

Let's start with the special case where the secondary fan only has a single chamber, and where the toric variety in that chamber is smooth.  We write $X$ for this toric varite.  Then $D_{\Cox}(S)=D(\sX)$ and each $\cO_{\Cox}(-d)$ is simply $\cO_{\sX}(-d)$.  Choose two elements $-d,-d'$ in the Bondal-Thomsen collection $\Theta$.  We must show several things:
\begin{enumerate}
    \item Exceptionality:  For any $-d\in \Theta$ we have
    \[
    \Hom_{X}(\cO_{X}(-d), \cO_{X}(-d)) = k \text{ and }
    \Ext^i_{X}(\cO_{X}(-d), \cO_{X}(-d)) = 0 \text { for $i>0$.}
    \]
    \item Orthogonality: For any $-d'<-d\in \Theta$ we have
        \begin{enumerate}
            \item

            $\Ext^i_{X}(\cO_{X}(-d), \cO_{X}(-d')) = 0$ for $i>0$ and
            \item  $\Hom(\cO_{X}(-d), \cO_{X}(-d'))=0$.
        \end{enumerate}
    \item Fullness:  The bundles $\cO_{X}(-d)$ with $-d\in \Theta$ generate the derived category.
\end{enumerate}
Exceptionality is trivial:
\[
\Hom_{X}(\cO_{X}(-d), \cO_{X}(-d)) \cong H^0(X, \cO_{X}(-d -(-d)) = H^0(X, \cO_{X}) = k^1
\]
because $X$ is a projective variety.  Also
\[
\Ext^i_{X}(\cO_{X}(-d), \cO_{X}(-d)) \cong H^i(X, \cO_{X}(-d -(-d)) = H^i(X, \cO_{X}) = 0
\]
because $X$ is a rational variety.

Fullness follows from the Hanlon--Hicks--Lazarev's proof of the Bondal's Conjecture (Conjecture \ref{conj:bondal}) which we saw back in \S\ref{subsect:bondalConjecture}.

Let us turn to orthogonality.  Part (b) of orthogonality is literally built into our definition of the ordering of the elements of $\Theta$; see Definition~\ref{defn:ordering}.  So orthogonality, part (a) is the meat of the argument.
\begin{lemma}
    Let $-d,-d'$ be two elements of the Bondal--Thomsen collection for $\sX$.  Assume that $-d'$ is anti-nef.  Then
    \[
    \Ext^i_{X}(\cO_{X}(-d), \cO_{X}(-d')) = 0 \text{ for all } i>0.
    \]
\end{lemma}
\begin{proof}
   Follows from Demazure vanishing.  Namely \daniel{fill in details}
\end{proof}

The following outline extends to the case where the secondary fan has one chamber, but where $X$ is simplicial but not smooth, with only standard changes required for working with the stack $\sX$ in place of $X$.

\bigskip

The case above is very special, however, as secondary fans generally have more than one chamber.  Nevertheless, it can provide something of a roadmap for the general proof.  Exceptionality will remain trivial.  Fullness will be due to a variant of a Hanlon--Hicks--Lazarev resolution of the diagonal, utilizing the  fact that the resolution of the diagonal is ``uniform'' for all of the $\sX_i$ associated to the Cox ring $S$ (see Corollary~\ref{cor:diagonalUniform}).  Orthogonality (b) will essentially follow from the definition of the ordering.  And so, as above, Orthogonality (a) will be the hardest part.

Let's examine what we would need to do in order to obtain Orthogonality.
Each $\cO_{\Cox}(-d)$ is defined as a pullback from one particular $\sX_i$.  For Orthogonality, we need to understand the relationship between two such bundles.  So let's say that $\cO_{\Cox}(-d)$ is the pullback of $\cO_{\sX_1}(-d)$ and $\cO_{\Cox}(-d')$ is the pullback of $\cO_{\sX_2}(-d')$.

We need to compute the $\Hom$ and $\Ext$ between these sheaves, and we thus need a way to compare sheaves pulled back from $\sX_1$ with sheaves pulled back from $\sX_2$.  That is, we need to compute:
\begin{align*}
\Ext^i_{D_{\Cox}(S)}(\cO_{\Cox}(-d),\cO_{\Cox}(-d')) &=
\Ext^i_{D_{\Cox}(S)}(\pi_1^*\cO_{\sX_1}(-d),\pi_2^*\cO_{\sX_2}(-d'))\\
\intertext{The Projection Formula allows us to swap the $\pi_1^*$ in the first factor to a $\pi_{1*}$ in the second factor.  This yields}
&=\Ext^i_{\sX_1}(\cO_{\sX_1}(-d),\pi_{1*}\pi_2^*\cO_{\sX_2}(-d'))\\
\intertext{So we can reduce the Orthogonality computation to a computation on $\sX_1$, but we will need to understand this weird-looking object $\pi_{1*}\pi_2^*\cO_{\sX_2}(-d')$.  But wait, we have seen this before!  It is the result of the Fourier--Mukai transform $\Phi_{21}$.  So we have}
&=\Ext^i_{\sX_1}(\cO_{\sX_1}(-d),\Phi_{21}\cO_{\sX_2}(-d')).
\end{align*}

And so the proof of Revised King's Conjecture will require us to understand the effect of Fourier--Mukai transforms on Bondal--Thomsen line bundles.  In general, understanding the Fourier--Mukai of a sheaf can be incredibly subtle or difficult.  But it turns out that, for the Bondal--Thomsen elements, the results of the Fourier--Mukai transforms are as simple as one could ever hope for.
\begin{lemma}[$\Theta$-Transform Lemma]\label{lem:PushPull}
Let $-d\in \Theta_X$ be an element whose image in $\Sigma_{GKZ}$ lies in the chamber corresponding to $\sX_i$.  For any $j$,
\[
\Phi_{ij}(\cO_{\sX_i}(-d)) = \cO_{\sX_j}(-d).
\]
Equivalently:
\[
\pi_{j*}\cO_{\Cox}(-d) = \cO_{\sX_j}(-d).
\]
\end{lemma}
In particular, the statement says the following:  start with a Bondal--Thomsen line bundle $\cO_{\sX_i}(-d)$ where $d$ comes from the chamber corresponding to $\sX_i$.  When you Fourier--Mukai transform this bundle to another chamber, you will get the corresponding Bondal--Thomsen line bundle on the nose.  In other words, $\cO_{\sX_i}(-d)$ will become $\cO_{\sX_j}(-d)$.

There are two miracles here, neither of which is obvious at first.  The first miracle is that the transform of this sheaf is a sheaf, i.e. that the higher pushforwards $R^i$ all vanish.  This is not generally true for Fourier--Mukai transforms, and so it is special for this case.  The second miracle is that the transform of a line bundle is still a line bundle.  Again, this is not generally true for Fourier--Mukai transforms.

In short, Lemma~\ref{lem:PushPull} is quite subtle, and it fails if one alters the hypotheses even
slightly.  We will explore this delicacy in more detail in Lecture~\ref{lec:15-proof-exceptionality}.
But we emphasize that the challenge in the lemma has nothing to do with stackiness, as the statement seems equally subtle when both $\sX_i$ and $\sX_j$ are smooth toric varieties.

\begin{remark}
  As far as we were able to determine, the $\Theta$-Transform Lemma does not appear to easily follow from known vanishing results from toric or birational geometry.  However, it would be interesting to explore this in greater detail.  \daniel{Michael asks if lev's simplification does this.  Come back to this point.}
\end{remark}

The next lecture will tackle the proof of the $\Theta$-Transform Lemma.  Before we dive into that, we want to note that the lemma almost immediately implies the Orthogonality statement we needed.

Combining the above computation with the $\Theta$-Transform Lemma, we conclude:
\[
\Ext^i_{D_{\Cox}(S)}(\cO_{\Cox}(-d),\cO_{\Cox}(-d')) =
\Ext^i_{\sX_1}(\cO_{\sX_1}(-d),\cO_{\sX_1}(-d')) = H^i(\sX_1, \cO_{\sX_1}(d-d')).
\]
Since $-d$ comes from the chamber $\Gamma_1$, it follows that $\cO_{\sX_1}(-d)$ is anti-nef; and since $-d'$ comes from the Bondal--Thomsen collection, it is a divisor with ``pure fractional coefficients''.  This is precisely the domain for Demazure Vanishing, which will thus immediately imply that all of these Ext groups vanish.  In short:  combining the $\Theta$-Tranform Lemma and Demazure Vanishing will immediately yield the Orthogonality statement we need.

\begin{example}\label{ex:hirzStrongBT}
Revisiting Example~\ref{ex:hirzGKZ} and Figure~\ref{fig:HirzSecondaryFan},
write $\pi_1\colon \tsX\to \cH_3$ and $\pi_2\colon \tsX \to \PP(1,1,3)$.
By Definition~\ref{defn:ThetaCox}, $\cO_{\Cox}(-1,0) = \pi_1^* \cO_{\cH_3}(-1,0)$.  Since $d=(-2,1)$ lies in the chamber corresponding to $\PP(1,1,3)$, we must use the fact that there is a natural corresponding element in $\Theta_{\PP(1,1,3)}$.
In this case, the map $\alpha\colon \ZZ^2\to \Cl(\PP(1,1,3))$ is given by $(a,b) \mapsto a+3b$ and thus $\cO_{\Cox}(2,-1) = \pi_2^* \cO_{\PP(1,1,3)}(\alpha(2,-1))=\pi_2^* \cO_{\PP(1,1,3)}(-1)$.
Here is a sample Hom computation:
\begin{align*}
\RHom(\cO_{\Cox}(-1,0), \cO_{\Cox}(2,-1))
&=\RHom(\pi_1^*\cO_{\cH_3}(-1,0), \pi_2^*\cO_{\PP}(2,-1)) & \text{by definition,}\\
&=\RHom(\cO_{\cH_3}(-1,0), \pi_{1*}\pi_2^*\cO_{\PP}(2,-1)) & \text{by adjunction,}\\
&=\RHom(\cO_{\cH_3}(-1,0), \cO_{\cH_3}(2,-1)) & \text{by Lemma~\ref{lem:PushPull},}\\
&=\RHom(\cO_{\cH_3}, \cO_{\cH_3}(3,-1))=0 & \text{by direct computation.}
\end{align*}
Note that the inverse computation is nonzero:
\begin{align*}
\RHom(\cO_{\Cox}(2,-1),  \cO_{\Cox}(-1&,0)) \\
\qquad
&=\RHom(\pi_2^*\cO_{\PP(1,1,3)}(-1), \pi_1^*\cO_{\cH_3}(-1,0))&\text{by definition,}\\
&=\RHom(\cO_{\PP(1,1,3)}(-1), \pi_{1*}\pi_2^*\cO_{\cH_3}(-1,0)) & \text{by adjunction,}\\
&=\RHom(\cO_{\PP(1,1,3)}(-1), \cO_{\PP(1,1,3)}(-1)) & \text{by \cref{lem:PushPull},} \\
&= \Bbbk^1 & \text{by direct computation.}
\end{align*}
Through similar computations for the other pairs, one can directly confirm that $\Theta$ forms a strong, exceptional collection.  Fullness requires an additional argument.
\end{example}

To summarize, the outline of the proof amounts to:
\begin{enumerate}
    \item  Combine the $\Theta$-Transform Lemma and Demazure Vanishing to obtain the necessary orthogonality statement .
    \item Use uniformity properties (Corollary~\ref{cor:diagonalUniform}) of the Hanlon-Hicks-Lazarev resolution of the diagonal to conclude that $\cO_{\Cox}(-d)$ with $-d\in \Theta$ generate $D_{\Cox}(S)$.
\end{enumerate}


{\color{blue} Paste in Example 4.5 from the King's paper, to demonstrate this point.  Remark on fullness.}

% Namely, we must compute $\RHom(\cO_{\Cox}(-d), \cO_{\Cox}(-d'))$ for two elements $-d,-d' \in \Theta$.
% By adjunction and the $\Theta$-Transform Lemma, this reduces to computing
% \[ \RHom(\cO_{\Cox}(-d), \cO_{\Cox}(-d'))
% \cong \RHom_{\sX_i}(\cO_{\sX_i}(-d), \cO_{\sX_i}(-d'))
% \cong H^*(\sX_i, \cO_{\sX_i}(d-d')).
% \]
% The element $d$ lies in the nef cone of $\sX_i$ and since $-d'$ is an element of $\Theta$, it can be written as a toric $\QQ$-divisor with all coefficients in $(-1,0]$.  The vanishing of the higher cohomology groups then follows from a stacky version of Demazure Vanishing for $\QQ$-divisors (\cref{thm:demazure}).

% \smallskip

% Fullness of the Bondal--Thomsen collection for each $\sX_i$ was proven in \cite{HHL}*{Corollary D} and \cite{FH}; the second step is to extend those results to show that $\Theta$ generates $D_{\Cox}$.  For this, we combine the fact that $\Theta_{\tsX}$ generates $D(\tsX)$ with \cref{lem:PushPull} and explicit computations regarding the behavior of Bondal--Thomsen bundles with respect to pushforward.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 15 (Patrick Kennedy-Hunt): Proof of revised King's conjecture, II: Exceptionality}\label{lec:15-proof-exceptionality}
As discussed in the previous section, when it comes to proving the orthogonality properties of the Bondal--Thomsen collection, the $\Theta$-Transform Lemma is the key.  Let us recall the setup.

Choose some degree $-d\in \Theta$ where $d$ lies in the chamber $\Gamma_1$ corresponding to $\sX_1$.  We have the following diagram:
\[
\xymatrix{
&\Gamma_{12}\ar[ld]_{p}\ar[rd]^{q}&\\
\sX_1&&\sX_2.
}
\]
And we must prove that
\[
R^\ell q_*(p^*\cO_{\sX_1}(-d)) =
\begin{cases}
\cO_{\sX_2}(-d) & \text{ if $\ell =0$}\\
0 & \text{ if $\ell > 0$}.
\end{cases}
\]
This breaks into fundamentally different parts:
\begin{itemize}
    \item  {\bf $R^0$-term:}  we must show that the $R^0q_*$-term is precisely the right line bundle.
    \item {\bf Vanishing:}  we must show a vanishing statement for the higher direct images $R^\ell q_*$ with $\ell>0$.
\end{itemize}
As we will try to demonstrate in the next example, these two parts are in tension with one another.

\begin{example}[Atiyah Flop]\label{ex:atiyahFlop}
This is a non-projective example, but it is instructive for thinking about the $\Theta$-Transform Lemma.  Consider the Cox ring $S=\Bbbk[x_0,x_1,y_0,y_1]$ with $\deg(x_i)=1$ and $\deg(y_j)=-1$.  The Koszul zonotope associated to this nonstandard graded ring (see Definition~\ref{defn:KoszulZonotope}) is the open interval $(-2,2)$ and so the Bondal--Thomsen collection consists of the divisors of degree $-1,0$ and $1$.

The secondary fan has two chambers: $\mathbb R_{\geq 0}$ and $\mathbb R_{\leq 0}$.
The first chamber corresponds to a threefold $Y_+ =[\Spec(S) - V(x_0,x_1) / \GG_m]$.  This is a $\PP^1$-bundle (coordinates $x_0,x_1$ on the fibers) over $\mathbb A^2$ (coordinates $y_0,y_1$ on the base).  The second chamber corresponds to $Y_- =[\Spec(S) - V(y_0,y_1) / \GG_m]$, which is a $\PP^1$-bundle (coordinates $y_0,y_1$ on the fibers) over $\mathbb A^2$ (coordinates $x_0,x_1$ on the base).
%The origin corresponds to $Y_0=\Spec(S_0)$ where $S_0=\Bbbk[x_0y_0, x_0y_1, x_1y_0, x_1y_1]$.
Let $\widetilde{Y}$ be the blowup of $Y_+$ at the line $V(y_0,y_1)$; one can check that this is isomorphic to the blowup of $Y_-$ at $V(x_0,x_1)$.   So we have a diagram:
\[
\xymatrix{
&\widetilde{Y}\ar[ld]_{p}\ar[rd]^{q}&\\
Y_+&&Y_-.
}
\]

As we often do, we will express sheaves on $Y_+$ and $Y_-$ via the corresponding $S$-modules.
We have $\Pic(Y_+)=\ZZ$, and for $d\in \ZZ$, we write $\cO_{Y_+}(d)$ for the line bundle associated to the free module $S(d)$.  Let us consider the Fourier--Mukai transforms $R_{q*}p^* \cO_{Y_+}(d)$ for all $d$.

We start by computing the $R^0$-term.  For any $d$ we have
\[
R^0q_*p^*\cO_{Y_+}(d) = \widetilde{S_{\geq d}}(d).
\]
Note that this is a line bundle if and only if $d\leq 0$,  More specifically, for $d\leq 0$ we have $S_{\geq d} = S$ and thus $R^0q_*\cO_{Y_+}(d) = \widetilde{S}(d) = \cO_{Y_-}(d)$.  But for $d>0$, we have $S_{\geq d} = \langle x_0,x_1\rangle^d$.  Since $\langle x_0,x_1\rangle$ is {\em not} a component of the irrelevant ideal on $Y_-$, this induces a nontrivial ideal sheaf on $Y_-$.   In particular, we have $R^0q_*\cO_{Y_+}(d) = \cO_{Y_-}(d)$ if and only if $d\leq 0$.  Thus, obtaining the correct $R^0$-term requires the initial line bundle to be ``{\em not too positive}''.

Let us now turn to the higher direct images.  The map $\widetilde{Y}\to Y_-$ is birational over $Y_- \setminus V(x_0,x_1)$, and the fibers over $V(x_0,x_1)$ are $1$-dimensional. Thus the $R^\ell q_*$ terms will automatically vanish for all $\ell > 1$, so we only need to be concerned about $R^1$.  A straightforward, if somewhat involved, computation shows that
\[
R^1q_*p^*\cO_{Y_+}(d) \ne 0 \iff H^1(Y_+, \cO_{Y_+}(d))\ne 0 \iff H^1(\PP^1, \cO_{\PP^1}(d)) \ne 0 \iff d>-2.
\]
So we will have the vanishing of the higher direct images if and only if  the initial line bundle is ``{\em not too negative}''.

Let us summarize.  Both conclusions--the correct $R^0$ and the vanishing of the higher direct images--are only satisfied for $d=0$ and $d=-1$. These are precisely the elements of the Bondal--Thomsen collection whose negatives lie in the chamber of the secondary fan corresponding to $Y_+$.
% \daniel{Need better notation here.}
% \[
% \begin{tabular}{c|c|c}
% &$R^0q_*$$&$R^1q_*$$\\\hline
% $d\geq 0$&$\widetilde{(x_0,x_1)^d}$$&$0$\\ \hline
% $d = -1$&$\cO_{Y_-}(-1)$&$0$\\ \hline
% $d\leq -2$&$\cO_{Y_-}(-1)$$&$H^1(\PP^1, \cO_{\PP^1}(d)) \otimes_k \cO_{pt}\ne 0$
% \end{tabular}
% \]
% The Bondal--Thomsen collection $\Theta$ consists of the degree $-1,0,1$ divisors.  By Definition~\ref{defn:ThetaCox}, we have $\cO_{\Cox}(-1)\ce p^* \cO_{Y_+}(-1)$ and $\cO_{\Cox}(1)\ce q* \cO_{Y_-}(1)$; and the pullbacks of $\cO_{Y_+}$ and $\cO_{Y-}$ coincide and are equal to $\cO_{\Cox}$.

% The $\Theta$-Transform Lemma implies that the Fourier--Mukai transform of $\cO_{Y_+}(d)$ from $Y_+$ to $Y_-$ will equal $\cO_{Y_-}(d)$ when $d=0$ or $d=-1$.
% A direct computation confirms that these are the {\em only} values of $d$ where this holds.  If $d > 0$ then the degree zero cohomology of the Fourier--Mukai transform will be the ideal sheaf of $(y_0,y_1)^d$, and if $d\leq -2$ then the degree one cohomology will be nonzero.
\end{example}


The example demonstrates that we require a delicate balance in order to obtain the conclusion of the $\Theta$-Transform Lemma.
A complete proof of the $\Theta$-Transform Lemma is given in \cite[\S4.3]{king}.  Instead of presenting the details of the proof in these notes, we will try instead to capture what aspects of the lemma are nontrivial.

Let us set some notation.  We start with a line bundle $\cO_{\sX_1}(-d)$ on $\sX_1$ and where $d$ lies in the chamber $\Gamma_1$ of the secondary fan.  This implies that $\cO_{\sX_1}(d)$ is a nef line bundle on $\sX_1$, and hence that $\cO_{\sX_1}(-d)$ is anti-nef.  Write $L:=p^* \cO_{\sX_1}(-d)$ for the corresponding line bundle on the graph $\Gamma_{12}$ and note that, since nefness is stable under pullback, $L$ is an anti-nef line bundle on $\Gamma_{12}$.



Let us start with the $R^0$-term.  We want to show that $q_*L \cong \cO_{\sX_2}(-d)$.  This is done in \cite[Lemma~4.14]{king} by comparing the global sections over each cone $\sigma$ in the fan $\Sigma_2$ corresponding to $\sX_2$.  We can compute the global sections in terms of lattice points satisfying certain inequalities involving piecewise linear support functions.  One key computation, given in\cite[Proposition~4.2]{king}, is that when $d$ lies in the chamber $\Gamma_1$, then the corresponding support function  for $\cO_{\sX_1}(-d)$ ``majorizes'' the support function for $\cO_{\sX_j}(-d)$ for any other $j$.  This shows that each section coming from $\cO_{\sX_2}(-d)$ also yields a section from $q_*L$.

The opposite direction is more subtle.  It relies on the fact that the Bondal--Thomsen line bundles can be expressed as toric divisors with purely fractional coefficients, and then utilizes this to create an inequality related to support functions of the form $\alpha \leq \alpha' \leq \lceil \alpha \rceil$.  The key trick is then:  if $\alpha$ is rational and $\alpha'$ is integral, then this inequality implies that $\alpha' = \lceil \alpha \rceil$.  Again, we refer to \cite[Lemma~4.14]{king} for the details, but we remark that the computation, while a bit longwinded, only relies on elementary facts about toric geometry and the behavior of the ceiling function.

The vanishing of the higher direct pushforwards is more involved.
The higher direct image sheaves $R^\ell q_*L$ encode the higher cohomology groups of $L$ restricted to the fibers of $q\colon \Gamma_{12} \to \sX_2$.   We would immediately obtain the vanishing of these if $L$ satisfied an appropriate positivty condition.  For instance, if $L$ were a nef line bundle then a relative version of Demazure vanishing would imply that the higher direct images vanish.  However $L$ is not nef:  in fact, as noted above, $L$ is anti-nef.

So to avoid having nonzero higher direct images, it is crucial that $L$ be {\em not too negative}.   Here is where the Bondal--Thomsen condition must come into play.  Recall that $L$ is the pullback of the Bondal--Thomsen element $\cO_{\sX_1}(-d)$, which is a divisor whose coefficients lie in $(-1,0]$.

If $L$ itself were an element of the Bondal--Thomsen collection of $\Gamma_{12}$, then Demazure Vanishing would again imply that the higher direct images vanish.  However, it is {\em not necessarily} the case that the pullback of a Bondal--Thomsen element is a Bondal--Thomsen element.  The pullback can acquire coefficients along exceptional divisors that are not in the range $(-1,0]$.

In fact, the $\Theta$-Transform Lemma holds true even if one replaces $\Gamma_{12}$ by some larger, birational toric cover.  This is the fundamentally most subtle aspect of the proof: we cannot easily control what happens to the coefficients of the toric divisor $L$ on $\Gamma_{12}$, and so it is difficult to utilize ``off-the-shelf'' vanishing statements, like Kawamata--Viehweg Vanishing.  The proof in \cite[\S4.3]{king} utilizes a polytope method, due to~\cite[Theorem~3.6]{altmann-immaculate}, to compute the higher cohomology of line bundles of the form $D-D'$ where both $D$ and $D'$ are nef.

\begin{remark}
    Often, the first proofs of an essential statement prove to be more complicated than necessary.  This happened with Hanlon--Hicks--Lazarev's proofs involving their resolutions, as their proof was later simplified by both \cite{BCHSY} and \cite{BH25}.  We expect that something similar will happen with the $\Theta$-Transform Lemma at some point, i.e. the proof outlined above will not be the ``final'' proof.
\end{remark}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Lecture 16 (John Nolan): Proof of Revised King Conjecture, III: Conclusion}

In this section, we will complete the proof of the Revised King Conjecture.  We recall our outline of what we need to prove.
\begin{enumerate}
    \item Exceptionality:  For any $-d\in \Theta$ we have
    \[
    \Hom_{X}(\cO_{X}(-d), \cO_{X}(-d)) = k \text{ and }
    \Ext^i_{X}(\cO_{X}(-d), \cO_{X}(-d)) = 0 \text { for $i>0$.}
    \]
    \item Orthogonality: For any $-d'<-d\in \Theta$ we have
        \begin{enumerate}
            \item

            $\Ext^i_{X}(\cO_{X}(-d), \cO_{X}(-d')) = 0$ for $i>0$ and
            \item  $\Hom(\cO_{X}(-d), \cO_{X}(-d'))=0$.
        \end{enumerate}
    \item Fullness:  The bundles $\cO_{X}(-d)$ with $-d\in \Theta$ generate the derived category.
\end{enumerate}

{\bf Proof of Exceptionality:}  Let $-d\in \Theta$ and say that $d$ lies in the chamber $\Gamma_i$.  Then we have
\begin{align*}
    \Hom_{D_{\Cox}(S)}(\cO_{\Cox}(-d), \cO_{\Cox}(-d)) &=\Hom_{D_{\Cox}(S)}(\pi_i^*\cO_{\sX_i}(-d), \pi_i^*\cO_{\sX_i}(-d)) &\text{By Definition~\ref{defn:ThetaCox}}\\
    &=\Hom_{\sX_i}(\cO_{\sX_i}(-d), \pi_{i*}\pi_i^*\cO_{\sX_i}(-d)) &\text{By Projection Formula}\\
    \intertext{By \cite{king}*{Lemma 3.7}, $\pi_{i*}\pi_i^*$ is just the identity.  So we have }
    &=\Hom_{\sX_i}(\cO_{\sX_i}(-d), \cO_{\sX_i}(-d)) &\text{By \cite{king}*{Lemma 3.7}}\\
    &=H^0(\sX_i, \cO_{\sX_i}) = k^1. &
\end{align*}
The last equality is because $\sX_i$ is integral and proper.\footnote{Strictly speaking, we are using a stacky version of this classical fact.  Namely, $H^0(\sX_i, \cO_{\sX_i})= H^0(X_i, \cO_{X_i})=k^1$ where the first equality is because $\sX_i\to X_i$ is a coarse moduli space, and the second equality is because $X_i$ is integral and proper. \daniel{Add citations here?}}
The computation for the higher Ext groups is similar and boils down to the fact that
\[
H^p(\sX_i, \cO_{\sX_i}) = H^p(X_i, \cO_{X_i}) = 0 \text{ for $p>0$},
\]
which follows from Demazure Vanishing or from Corollary~\ref{cor:BTNoCohom}.

{\bf Orthogonality (a)}:  Choose $-d$ and $-d'$ in $\Theta$ and let $\Gamma_i$ be a chamber whose closure contains $d$  and let $\Gamma_j$ be a chamber whose closure contains $d'$.  We have
\begin{align*}
      \Ext^p{D_{\Cox}(S)}(\cO_{\Cox}(-d), \cO_{\Cox}(-d')) &=\Hom_{D_{\Cox}(S)}(\pi_i^*\cO_{\sX_i}(-d), \pi_j^*\cO_{\sX_i}(-d')) &\text{By Definition~\ref{defn:ThetaCox}}\\
    &=\Ext^p{\sX_i}(\cO_{\sX_i}(-d), \pi_{i*}\pi_j^*\cO_{\sX_i}(-d')) &\text{By Projection Formula}\\
    &=\Ext^p{\sX_i}(\cO_{\sX_i}(-d), \cO_{\sX_i}(-d')) &\text{Lemma~\ref{lem:PushPull}}\\
    &=H^p(\sX_i, \cO_{\sX_i}(d-d'))=0. &
\end{align*}
The final equality follows from Proposition~\ref{prop:Demauzre},\footnote{We are using the stacky version of that proposition.  But again, the shift from varieties to stacks is mostly formal in this setting.  See \cite[Theorem 2.11]{king} for the necessary stacky statement.}noting that $d$ is a nef class on $\sX_i$ because $d$ lies in the closure of the chamber $\Gamma_i$.

{\bf Orthogonality (b)}: This follows from Definition~\ref{defn:BTcollection}.

{\bf Fullness:}  We now turn to proving fullness.  We need to show:

\begin{prop}\label{prop:generation}
    The Cox category $D_{\Cox}(S)$ is generated by $\cO_{\Cox}(-d)$ with $-d \in \Theta$.
\end{prop}
\begin{proof}
By Bondal's Conjecture, the line bundles corresponding Bondal--Thomsen degrees generate $D(\sX_j)$ for all $j$.  And by the $\Theta$-Transform Lemma, the line bundles $\cO_{\Cox}(-d)$ with $-d\in \Theta$ pushforward to the Bondal--Thomsen line bundles on $\sX_j$ for all $j$.  In other words, the line bundles  $\cO_{\Cox}(-d)$ with $-d\in \Theta$  push forward to a generating set on $D(\sX_j)$ for each $j$.  Since $D_{\Cox}(S)$ was built as the ``union'', in some sense, of the $D(\sX_j)$, this suggests that that $D_{\Cox}(S)$ will be generated by $\cO_{\Cox}(-d)$ with $-d \in \Theta$.  

But to make that precise, we require one additional fact.  There are roughly two ways to proceed.

The most satisfying approach is to enrich $D_{\Cox}(S)$ to a dg-category, and then prove that the Hanlon--Hicks--Lazarev resolution of the diagonal induces an dg-category resolution of the diagonal for $D_{\Cox}(S)$.  This is true, and is implied by Theorem~\ref{thm:resDiagCoxVague}, but that proof involves a fair amount of juggling derived categories.  That said, this approach is satisfying becuase it ``explains'' the mysterious uniformity of the Hanlon--Hicks--Lazarev resolution of the diagonal observed back in Corollary~\ref{cor:diagonalUniform}, where the resolution is uniform for the $X_i$ appearing in the secondary fan.

Another satisfying method would be the following.  By the proof Bondal's Conjecture we know that the Bondal--Thomsen collection $\Theta_{\widetilde{\sX}}$ for $\widetilde{\sX}$ generates $D(\widetilde{\sX})$.
If $D_{\Cox}(S)\subseteq D(\widetilde{\sX})$ is an admissible subcategory, then we could apply the projection functor $p\colon  D(\widetilde{\sX}) \to D_{\Cox}(S)$, to conclude that $p(\Theta_{\widetilde{\sX}})$ generates $D_{\Cox}(S)$.  And then, by utilizing a standard fact that ``Bondal--Thomsen pushes forward to Bondal--Thomsen'' as in, e.g. \cite[Proposition 2.28]{king}, we get the desired generation result.  Again, this is true, but we will not prove it: see~\cite[Corollary 5.5]{king}.

The most direct proof of the generation result is the following,  which follows \cite[Proposition 5.1]{king}.  We start by choosing some $m\in M\otimes \QQ$ and we write $-\widetilde{d}$ for the corresponding Bondal--Thomsen element in $ \Cl(\widetilde{\sX})$  and $-d$ for the corresponding Bondal--Thomsen element in $ \Cl(\widetilde{\sX})$.\footnote{So using notation from \S\ref{lec:6-bondal-thomsen}, we would have that $-d = \deg \alp(m)$.}  By \cite[Proposition 2.28]{king}, $\pi_{j*}(\cO_{\widetilde{\sX}}(-\widetilde{d}) = \cO_{\sX_j}(-d)$.  If we choose $j$ so that $\cO_{\Cox}(-d)=\pi_j^* \cO_{\sX_j}(-d)$, then by adjunction we have
\begin{align*}
\Hom_{\widetilde{\sX}}(\cO_{\Cox}(-d), \cO_{\widetilde{\sX}}(-\widetilde{d}))
&=
\Hom_{\widetilde{\sX}}(\pi_j^* \cO_{\sX_j}(-d), \cO_{\widetilde{\sX}}(-\widetilde{d}))\\
&=
\Hom_{\widetilde{\sX}}(\cO_{\sX_j}(-d), \pi_{j*} \cO_{\widetilde{\sX}}(-\widetilde{d}))\\
&=
\Hom_{\widetilde{\sX}}(\cO_{\sX_j}(-d), \cO_{\sX_j}(-d)).
\end{align*}
This last group contains the identity morphism, and so there exists a corresponding $f\colon \cO_{\Cox}(-d)\to \cO_{\widetilde{\sX}}(-\widetilde{d})$.  Let $C(f)$ be the cone of $f$.  By the $\Theta$-Transform Lemma and \cite[Proposition 2.28]{king}, if we push this forward to $\sX_i$ for any $i$, then we will get
\[
\pi_{i*}(C(f)) = \big[ \cO_{\sX_i}(-d) \overset{\pi_{i*}(f)}{\longrightarrow
}\cO_{\sX_i}(-d)\big].
\]
Since the $\pi_{i*}(f)$ maps all agree on the torus (where the $\sX_i$ and $\widetilde{\sX}$ are all isomorphic), these all agree with the identity map on the dense torus.  But a map from a line bundle to itself on $\sX_i$ is given by a constant function, and so if it is the identity on a dense open subset, then it is the identity morphism.  In particular, $\pi_{i*}(C(f))=0$ for all $i$.

We define $\mathcal Q$ as the set of objects in $D(\widetilde{\sX})$ where $\pi_{i*}\cE = 0$. We also define the left-orthogonal subcategory of $\mathcal Q$ as
\[
\phantom{X}^{\perp}\mathcal Q := \{ \cE \in D(\widetilde{\sX}) | \Hom(\cE, \cF) = 0 \text{ for all }\cF \in \mathcal Q\}.
\]
So we have shown that the object $C(f)$ lies in $\mathcal Q$.  We also have that $D_{\Cox}(S) \subseteq \phantom{X}^{\perp}\mathcal Q$ by a simple adjunction computation.  It follows that the composition $D_{\Cox}(S) \to D(\widetilde{\sX}) \overset{\rho}{\to} D(\widetilde{\sX})/ \mathcal Q$ is fully faithful.  Thus, to prove that the $\cO_{\Cox}(-d)$ generate $D_{\Cox}(S)$, it suffices to prove that they generate $D(\widetilde{\sX})/ \mathcal Q$.  Since $C(f) \in \mathcal Q$, it follows that $\rho(\cO_{\widetilde{\sX}}(-\widetilde{d})) = \rho(\cO_{\Cox}(-d))$.  And since the $\cO_{\widetilde{\sX}}(-\widetilde{d})$ generate $D(\widetilde{\sX})$ their images--which equal the Bondal--Thomsen collection for the Cox category--generate $D(\widetilde{\sX})/ \mathcal Q$.
\end{proof}


\ifdefined\whole
\else
\bibliographystyle{plain}
\bibliography{Bibliography}
\end{document}
\fi
